\documentclass[12pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{array,booktabs,enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[capitalize,nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

\newcommand{\eps}{\varepsilon}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Pb}{\mathbb{P}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cX}{\mathcal{X}}
\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\supp}{supp}
\DeclareMathOperator{\spn}{sp}
\DeclareMathOperator{\Out}{Out}
\DeclareMathOperator{\BR}{BR}

\title{\textbf{Uniform Equilibrium from an Augmented Metastable Tree\\under Robust Nodewise Irreducibility}}
\author{Pedro Aldighieri}
\date{March 2026}

\begin{document}
\maketitle



\begin{abstract}
Neyman's problem asks whether every finite stochastic game admits a uniform
$\eps$-equilibrium. The full conjecture remains open. This paper proves the
\emph{downstream} part of the compact-tree route under explicit conditional input:
we assume that a finite universal $\eta$-tree representation is available together
with the first-exit controller realization attached to that tree, and we show that
this input yields a public finite-memory uniform $\eps$-equilibrium under a robust
nodewise irreducibility hypothesis.

Version~14 keeps the structural terminal fix and the strategy-independent
launched-block repair, and adds the missing full scheduled-block payoff identity.
Every former terminal boundary label $b$ is replaced by a \emph{degenerate
terminal node} $T_b$, a leaf of the universal tree with a single internal
absorbing state, no exits, constant per-stage payoff vector $w(b)$, trivial
bookkeeping kernel, and exact Bellman certificate
\[
g_{T_b}=w(b),
\qquad
h_{T_b}\equiv 0.
\]
If play exits an ordinary node through label $b$, public routing continues at
$T_b$ and the frozen block schedule keeps running until the horizon is exhausted.
Moreover, each launched block has a publicly fixed scheduled boundary and its
payoff is evaluated over all scheduled stages. The live part ends at the first
cemetery hit; if that hit occurs before the scheduled boundary, the remaining
cemetery part of the block is filled with the fixed continuation rate $v(b)$
attached to the public exit label. Thus the compliant and deviating comparisons
are carried out on common scheduled blocks of common length, the cemetery
completion is a common addend once the public exit record is fixed, and the
regret estimate is concentrated on the live first-exit segment controlled by the
renewal-reward identity.

To keep the convex occupation package and the genuine executed dynamics separate,
the paper distinguishes two kernels. The \emph{bookkeeping kernel} lives on
$\Xi_C$ alone and folds exit mass back to $\Xi_C$ through the internal restart map
$\rho_C$; it is used only to define the convex occupation package
$\bar\mu_C^*=(\mu_C^*,\beta_C^*)$. The \emph{executed augmented kernel} lives on
$\Xi_C^{\mathrm{aug}}$ and has absorbing cemetery states; it is used for
condition~\textnormal{(a)}, for the bias bound, and for the live Bellman
estimate. The full launched-block payoff is obtained by adjoining to the live
augmented reward the explicit cemetery completion on the remaining scheduled
stages.

At each ordinary node and for frozen continuation values, every player faces a
finite communicating average-reward MDP on the internal state space with
continuation rewards at exits. At each degenerate terminal node the local game is
one-state and exact. The normalized bias is unique after fixing one reference
coordinate, local stationary Nash equilibria exist by Kakutani, and the global
frozen-continuation correspondence has a fixed point. Using the first-exit
controller realization supplied by the tree input, the realized profile satisfies a
regret bound of the form
\[
\eta + C_\eta\delta + \frac{K_\eta}{T}.
\]
Choosing the parameters in that order yields the theorem.
\end{abstract}



\tableofcontents

\section{Introduction}

\subsection{Neyman's problem}

Shapley introduced stochastic games in 1953 and proved existence of stationary
equilibria for the discounted evaluation \cite{Shapley1953}. The long-run average
evaluation is much subtler. For zero-sum stochastic games, Mertens and Neyman
proved existence of the uniform value \cite{MertensNeyman1981}. For two-player
non-zero-sum stochastic games, Vieille established the existence of uniform
$\eps$-equilibria \cite{Vieille2000I,Vieille2000II}. Beyond two players the full
problem remains open; see Neyman's survey chapter, Solan's chapter on the
multi-player problem, Vieille's survey, and the handbook treatment
\cite{Neyman2003,Solan2003,Vieille2002,MertensSorinZamir2003}. Positive results
are known in special subclasses, including three-player absorbing games
\cite{Solan1999}, correlated equilibrium constructions \cite{SolanVieille2002},
cyclic Markov equilibria phenomena \cite{FleschThuijsmanVrieze1997}, and extensions
to broader state-space settings \cite{Nowak2003}.

The central question is:
\begin{quote}
\textbf{Neyman's open problem.}
For every finite stochastic game and every $\eps>0$, does there exist a strategy
profile that is an $\eps$-equilibrium simultaneously for all sufficiently large
finite horizons?
\end{quote}

This paper does not claim to settle the conjecture in full generality. Its scope
is narrower and more precise: we start from the finite universal $\eta$-tree
representation produced by the route-D' reduction, together with its first-exit
controller realization, and show that once that input is available the remainder
of the route is correct under a robust nodewise irreducibility condition. The
point of the rewrite is not to alter the theorem's scope but to make every
definition used downstream mathematically correct and every stated proof complete.

\subsection{Main theorem}

We first record the standing scope. The compact asymptotic tree representation and
its first-exit controller realization are inputs to the present paper.

\begin{assumption}[Standing tree input]
\label{ass:tree-input}
For every $\eta\in(0,1)$, the game is endowed with a finite universal
$\eta$-tree representation as specified in
\Cref{ass:node-data,ass:controller-input}. All theorems in
Sections~\ref{sec:bookkeeping}--\ref{sec:proof-main} are proved relative to that
finite-dimensional input.
\end{assumption}

Under this standing input the paper proves the following theorem.

\begin{theorem}[Main theorem]
\label{thm:main}
Let
\[
G=(N,S,(A_i)_{i\in N},u,P)
\]
be a finite stochastic game, and assume \Cref{ass:tree-input}. Assume further
that condition~\textnormal{(a)} from \Cref{cond:a} holds for the augmented node
kernels of the universal $\eta$-trees. Then for every $\eps>0$ there exist a
public finite-memory strategy profile $\sigma^\eps$ and $T_0\in\N$ such that for
every $T\ge T_0$, every initial state $s\in S$, every player $i\in N$, and every
unilateral deviation $\tau_i$,
\[
\gamma_i^T(s,\sigma^\eps)
\ge
\gamma_i^T\bigl(s,(\tau_i,\sigma^\eps_{-i})\bigr)-\eps.
\]
In particular, every finite stochastic game equipped with a universal
$\eta$-tree representation and first-exit controller realization satisfying
condition~\textnormal{(a)} admits a public finite-memory uniform
$\eps$-equilibrium for every $\eps>0$.
\end{theorem}

\begin{remark}
The theorem is intentionally scoped to the downstream part of the compact-tree
route. The full Neyman conjecture remains open because the route still requires,
in the background, construction of the universal $\eta$-tree representation and
its realization map for an arbitrary game. The purpose of the present rewrite is
to show that the remaining argument from that representation to a uniform
equilibrium is mathematically correct once the earlier blockers and the
renewal-reward bookkeeping repair are in place.
\end{remark}


\subsection{The v14 repair}

Version~14 keeps the v10-v13 frozen-continuation, local-Nash,
bias-normalization, augmented-kernel, routing, terminal-node, renewal-reward,
and launched-block repairs, and adds the missing full scheduled-block payoff
identity.

\begin{enumerate}[label=\textnormal{(\arabic*)},leftmargin=2.4em]
\item The bias normalization is linearized. Every local bias is normalized by the
fixed reference coordinate $h_{i,C}(\xi_C^\circ)=0$, not by the non-convex
condition $\min_\xi h_{i,C}(\xi)=0$.
\item Every irreducibility, hitting-time, and bias-span statement is formulated
for the genuine absorbing augmented kernel on
$\Xi_C^{\mathrm{aug}}=\Xi_C\sqcup\partial B_C$, not for the sub-stochastic
internal kernel.
\item Every former terminal boundary label $b$ is replaced by a degenerate
terminal node $T_b$. This node has one internal absorbing state, no exits,
constant per-stage payoff vector $w(b)$, and trivial certificate
$g_{T_b}=w(b)$, $h_{T_b}=0$.
\item A launched block in node $C$ has a publicly announced cap $L$ and hence a
fixed scheduled interval of length $L$. Inside that interval the live path may
hit a cemetery state at a first live time $\tau\le L$ and emit at most one
boundary label, but the block boundary itself remains at the scheduled cap.
\item The bookkeeping kernel and the executed intrablock dynamics are kept
separate. The restart kernel $\rho_C$ belongs only to the bookkeeping occupation
package, is never an executed transition after a cemetery hit, and is fixed by
the bookkeeping convention
\[
\rho_C(\cdot\mid b)=\delta_{\xi_C^\circ}
\qquad (b\in B_C).
\]
In the executed augmented dynamics the unique boundary label, if any, is merely
recorded until the next scheduled block launch.
\item The local payoff identity remains a renewal-reward identity on the live
first-exit segment. If a block is launched with cap $L$, then its live duration
is the random first-exit time $\tau\le L$, and the correct local target is
\[
g_{i,C}^*
=
\frac{\E[\widetilde U_{i,C,L}]}{\E[\tau_{C,L}]},
\]
not $\E[\widetilde U_{i,C,L}/L]$. The only possible extra bookkeeping term is the
restart-bias
\[
\sum_{\xi'}(R_C\beta_C^*)(\xi')h_{i,C}^*(\xi'),
\]
and here it vanishes because every bookkeeping restart returns to the reference
state $\xi_C^\circ$ where $h_{i,C}^*(\xi_C^\circ)=0$.
\item The global regret comparison is carried out on \emph{full}
scheduled-block payoffs. For every launched block $B$ and every evaluation
profile $\varsigma$ one writes
\[
U_i^{\mathrm{full}}(B;\varsigma)
=
\widetilde U_i(B;\varsigma)+U_i^{\mathrm{cem}}(B),
\]
where $\widetilde U_i(B;\varsigma)$ is the augmented live payoff and
$U_i^{\mathrm{cem}}(B)$ is the absorbed cemetery completion on the remaining
scheduled stages after the public exit record of $B$ has been fixed. Hence both
the compliant and deviating comparisons are performed on the same launched block
of the same scheduled length $|B|$, the cemetery completion is a common addend
in the subtraction, and the only nontrivial incentive estimate is the live
renewal-reward estimate.
\item The ambient compact boxes are depth-sensitive. For each node $C$, gains are
confined to $[0,d_\eta(C)]$ and boundary continuation values to
$[0,d_\eta(C)-1]^N$, where $d_\eta(C)$ is the remaining tree depth below $C$.
This is the correct box because each node contributes at most one unit of stage
payoff and continuation values propagate through only finitely many further
layers.
\item The finitely many prelude blocks before the frozen tail scale $M_*$ are not
covered by the tail block-regret estimate. Their total contribution is therefore
peeled off once and for all into the $K_\eta/T$ remainder term.
\item The launched block schedule never stops before horizon $T$. After an exit
into a degenerate terminal node, subsequent scheduled blocks are simply the
trivial capped blocks of that node. Hence terminal behavior is covered by the
same routing, realization, telescoping, and regret estimates as all other
nodes, and no special post-terminal accounting is needed.
\end{enumerate}

\subsection{Roadmap}


Section~\ref{sec:model} recalls the game model and states the finite-dimensional
node data used by the compact-tree route. Section~\ref{sec:bookkeeping}
introduces the bookkeeping kernel and proves the graph theorem for the internal
occupation package. Section~\ref{sec:local} formulates the local game on the
genuine augmented state space and establishes local best-response and local
equilibrium existence. Section~\ref{sec:global} defines the global correspondence
with frozen continuation values and proves a Kakutani fixed point theorem.
Section~\ref{sec:realization} defines first-exit blocks and realizes the fixed
point by public finite-memory block controllers. Section~\ref{sec:proof-main}
proves the augmented-kernel bias bound, the deviation-value Lipschitz lemma, the
blockwise Bellman bound, and finally \Cref{thm:main}. The appendices record the
finite-MDP facts and the final aggregation bookkeeping.

\section{Model and standing asymptotic input}
\label{sec:model}

\subsection{Finite stochastic games}

A finite stochastic game is a tuple
\[
G=(N,S,(A_i)_{i\in N},u,P)
\]
where $N=\{1,\dots,n\}$ is the finite set of players, $S$ is the finite state
space, $A_i(s)$ is the finite action set of player $i$ at state $s$, the stage
payoff of player $i$ is a function
\[
u_i:S\times \prod_{j\in N}A_j(s)\to [0,1],
\]
and the transition kernel is
\[
P(\cdot\mid s,a)\in \Delta(S)
\qquad (s\in S,\ a\in \prod_{j\in N}A_j(s)).
\]
The public history at stage $t$ is
\[
h_t=(s_1,a_1,s_2,a_2,\dots,s_t).
\]
A behavioral strategy of player $i$ assigns to every public history $h_t$ a
probability distribution on $A_i(s_t)$.

For a horizon $T\ge 1$, an initial state $s$, and a profile $\sigma$, the average
payoff of player $i$ is
\[
\gamma_i^T(s,\sigma)
=
\E_{s,\sigma}\Bigl[\frac1T\sum_{t=1}^T u_i(s_t,a_t)\Bigr].
\]
We write
\[
\|u\|_\infty
:=
\max_{i\in N}\max_{s\in S}\max_{a\in\prod_{j\in N}A_j(s)} |u_i(s,a)|.
\]
Under the standing normalization $u_i\in[0,1]$, one has $\|u\|_\infty\le 1$.

\begin{definition}
A profile $\sigma$ is an \emph{$\eps$-equilibrium for horizon $T$} if for every
player $i$, every initial state $s$, and every unilateral deviation $\tau_i$,
\[
\gamma_i^T(s,\sigma)
\ge
\gamma_i^T\bigl(s,(\tau_i,\sigma_{-i})\bigr)-\eps.
\]
It is a \emph{uniform $\eps$-equilibrium} if there exists $T_0$ such that the same
inequality holds for every $T\ge T_0$.
\end{definition}

\subsection{Node data from the tree representation}

The present paper starts after the route-D' reduction has produced a finite rooted
universal $\eta$-tree. We record exactly the node data used later.

\begin{assumption}[Finite node data]
\label{ass:node-data}
Fix $\eta\in(0,1)$. The universal $\eta$-tree $\cT_\eta$ is finite. Its nodes are
of two kinds: ordinary nodes and degenerate terminal nodes. Every node
$C\in \cT_\eta$ carries the following data.
\begin{enumerate}[label=\textnormal{(D\arabic*)},leftmargin=2.8em]
\item A finite phase-state set
\[
\Xi_C=\bigsqcup_{k\in\mathbb Z/d_C\mathbb Z}\{k\}\times S_C^k
\]
and a distinguished reference state $\xi_C^\circ\in\Xi_C$.
\item For each player $i$ and phase-state $\xi\in\Xi_C$, a finite action set
$A_i(\xi)$.
\item A finite boundary set $B_C$ and a successor map $b\mapsto C[b]$ sending
boundary states to child nodes of $\cT_\eta$. Whenever the earlier route would
have attached a terminal label $b$, the enlarged tree now contains the
corresponding degenerate terminal child $T_b:=C[b]$.
\item Internal transition coefficients
\[
P_C^0(\xi'\mid \xi,a)\in[0,1],
\qquad \xi,\xi'\in \Xi_C,
\ a\in \prod_{j\in N}A_j(\xi),
\]
and exit coefficients
\[
\lambda_C(b\mid \xi,a)\in[0,1],
\qquad b\in B_C,
\]
such that
\[
\sum_{\xi'\in\Xi_C}P_C^0(\xi'\mid \xi,a)+\sum_{b\in B_C}\lambda_C(b\mid\xi,a)=1.
\]
\item A bookkeeping restart kernel fixed by the convention
\[
\rho_C(\cdot\mid b)=\delta_{\xi_C^\circ}
\qquad (b\in B_C).
\]
This kernel is used only in the internal bookkeeping chain from
Section~\ref{sec:bookkeeping}; it is not part of the executed first-exit
dynamics. In particular every bookkeeping restart returns to the reference
state $\xi_C^\circ$.
\item A universal bias box constant $B_\eta^0<\infty$ such that every local
Bellman certificate used later can be normalized inside
$[-B_\eta^0,B_\eta^0]^{\Xi_C}$.
\end{enumerate}

If $C=T$ is a degenerate terminal node, then
\[
\Xi_T=\{\xi_T^\circ\},
\qquad
B_T=\varnothing,
\qquad
A_i(\xi_T^\circ)\text{ is a singleton for every }i,
\]
the unique internal transition is absorbing,
\[
P_T^0(\xi_T^\circ\mid \xi_T^\circ,a)=1,
\]
and for the unique action profile $a^\dagger$ one has
\[
u_i(\xi_T^\circ,a^\dagger)=w_i(T)\in[0,1].
\]
Thus $T$ is a one-state absorbing leaf with trivial bookkeeping kernel and exact
local certificate
\[
g_{i,T}=w_i(T),
\qquad
h_{i,T}\equiv 0.
\]
For a boundary label $b$ leading to $T_b$, we also write $w(b):=w(T_b)$.
\end{assumption}

\begin{remark}[Tree-depth bookkeeping]
\label{rem:tree-depth}
For each degenerate terminal node $T$, set $d_\eta(T):=1$. For an ordinary node
$C\in\cT_\eta$, define recursively
\[
d_\eta(C)
:=
\begin{cases}
1, & B_C=\varnothing,\\[0.3em]
1+\max_{b\in B_C} d_\eta(C[b]), & B_C\neq \varnothing.
\end{cases}
\]
Thus $d_\eta(C)$ is the maximal number of node layers on a path beginning at $C$.
Set
\[
D_\eta:=\max_{C\in\cT_\eta} d_\eta(C)<\infty.
\]
Whenever $b\in B_C$, the remaining depth below $b$ is at most $d_\eta(C)-1$.
Accordingly, boundary continuation values will always be stored in
$[0,d_\eta(C)-1]^N$, and the corresponding local gains will lie in
$[0,d_\eta(C)]$. In particular a cemetery-routing path contains at most
$D_\eta-1$ strict child moves, hence certainly at most $D_\eta$ cemetery exits.
Once play enters a degenerate terminal node, no further cemetery exit can occur.
\end{remark}

\begin{assumption}[First-exit controller realization]
\label{ass:controller-input}
Fix $\eta\in(0,1)$ and a node $C\in\cT_\eta$. For every stationary mixed kernel
$\sigma_C\in\Sigma_C$ and every cap $L\ge 1$, the universal
$\eta$-tree representation supplies a public finite-memory first-exit block
controller $\mathcal R_{C,L}^{\sigma_C}$. During every live stage with current
phase-state $\xi\in\Xi_C$, the compliant action profile is sampled from the
prescribed stationary kernel $\sigma_C(\cdot\mid\xi)$; the additional public
memory is only an implementation device and does not alter the one-step
coefficients on $\Xi_C$. The controller has the following properties.
\begin{enumerate}[label=\textnormal{(R\arabic*)},leftmargin=2.8em]
\item If the controller starts from an entry phase-state in $\Xi_C$, its live
path evolves on the genuine augmented state space
$\Xi_C^{\mathrm{aug}}=\Xi_C\sqcup\partial B_C$ until the stopping time
\[
\tau_{C,L}
:=
\inf\{t\ge 1:X_t\in\partial B_C\}\wedge L.
\]
This $\tau_{C,L}$ is the live first-exit segment used in the local
renewal-reward estimates. When the controller is embedded into a launched
scheduled block of cap $L$, the right boundary of that block remains the
announced time $L$; if $\tau_{C,L}<L$ and $X_{\tau_{C,L}}=\partial_b$, the public
memory simply stays in the absorbed intrablock state $\partial_b$ until the
scheduled boundary.
\item At most one boundary label is emitted. If $\tau_{C,L}<L$ and
$X_{\tau_{C,L}}=\partial_b$, then that unique label is $b$, and it is stored in
public memory until the scheduled boundary.
\item Let $N_{C,L}(\xi,a)$ be the number of live stages
$t\in\{0,\dots,\tau_{C,L}-1\}$ at which $(X_t,A_t)=(\xi,a)$, and let
$I_{C,L}(b):=\1_{\{X_{\tau_{C,L}}=\partial_b\}}$. Define the empirical live-time
rates
\[
\widehat\mu_{C,L}^{\mathrm{rate}}(\xi,a):=\frac{N_{C,L}(\xi,a)}{\tau_{C,L}},
\qquad
\widehat\beta_{C,L}(b):=\frac{I_{C,L}(b)}{\tau_{C,L}}.
\]
Then, uniformly over entry states, there exists $K_C(\sigma_C)<\infty$ such that
\begin{equation}
\label{eq:controller-input-occ}
\E\Bigl[
\bigl\|(\widehat\mu_{C,L}^{\mathrm{rate}},\widehat\beta_{C,L})
-
\bar\mu_C^\sigma
\bigr\|_1
\Bigr]
\le \frac{K_C(\sigma_C)}{\sqrt L}.
\end{equation}
\item For every continuation vector
$v_C(\cdot)\in[0,d_\eta(C)-1]^{B_C\times N}$, the controller's total augmented
live reward is
\[
\widetilde U_{i,C,L}
:=
\sum_{t=0}^{\tau_{C,L}-1} u_i^t
+
\sum_{b\in B_C}I_{C,L}(b)\,v_{i,C}(b).
\]
\item Uniformly over entry states and players,
\begin{equation}
\label{eq:controller-input-renewal}
\left|
\frac{\E[\widetilde U_{i,C,L}]}{\E[\tau_{C,L}]}
-
\left(
\sum_{(\xi,a)\in\Omega_C}\mu_C^\sigma(\xi,a)u_i(\xi,a)
+
\sum_{b\in B_C}\beta_C^\sigma(b)v_{i,C}(b)
\right)
\right|
\le \frac{K_C(\sigma_C)}{\sqrt L}.
\end{equation}
\end{enumerate}
\end{assumption}

\begin{remark}
If $C=T$ is degenerate terminal, then the controller
$\mathcal R_{T,L}^{\sigma_T}$ is the trivial capped block of length $L$: it stays
at $\xi_T^\circ$ throughout, emits no boundary label, satisfies
$\tau_{T,L}=L$ almost surely, and yields
$\widetilde U_{i,T,L}=L\,w_i(T)$ exactly. Hence
\eqref{eq:controller-input-occ} and \eqref{eq:controller-input-renewal} hold with
zero error at degenerate terminal nodes.
\end{remark}

\subsection{Pure and mixed stationary kernels inside a node}

Fix a node $C$. A \emph{pure stationary selector} of player $i$ in node $C$ is a
map
\[
f_i: \Xi_C\to \bigsqcup_{\xi\in\Xi_C}A_i(\xi)
\quad\text{with }f_i(\xi)\in A_i(\xi).
\]
The finite set of such selectors is denoted by $F_{i,C}$. A \emph{stationary
mixed kernel} of player $i$ is an element of
\[
\Sigma_{i,C}:=\prod_{\xi\in\Xi_C}\Delta(A_i(\xi)).
\]
We write $\Sigma_C:=\prod_{i\in N}\Sigma_{i,C}$.

\begin{remark}
A point of $\Sigma_{i,C}$ may be viewed either as a statewise mixed-action kernel
or, equivalently, as a product distribution over the finite selector set
$F_{i,C}$. We work with statewise mixed kernels because the deviation MDP
coefficients are affine in those kernels; this is the precise form needed later.
The local equilibrium existence result in Section~\ref{sec:local} is equivalent to
Nash's theorem for the finite selector game.
\end{remark}

\section{The bookkeeping node system and the linear exit map}
\label{sec:bookkeeping}

\subsection{Bookkeeping kernel and balance equations}

Fix a node $C\in\cT_\eta$. This section does \emph{not} describe the executed
block dynamics. It records only the internal bookkeeping chain used to define the
convex occupation package. Exit mass is instantaneously re-injected into internal
states through $\rho_C$, so the bookkeeping chain lives on $\Xi_C$ alone.

For a stationary mixed kernel $\sigma_C\in\Sigma_C$, define the induced internal
kernel
\[
Q_C^{\sigma}(\xi'\mid \xi)
:=
\sum_{a\in\prod_j A_j(\xi)} \sigma_C(a\mid \xi)
P_C^0(\xi'\mid \xi,a),
\]
and the induced exit kernel
\[
\Lambda_C^{\sigma}(b\mid\xi)
:=
\sum_{a\in\prod_j A_j(\xi)}\sigma_C(a\mid\xi)\lambda_C(b\mid\xi,a).
\]
The corresponding bookkeeping kernel on $\Xi_C$ is
\begin{equation}
\label{eq:bookkeeping-kernel}
\widetilde Q_C^{\sigma}(\xi'\mid \xi)
=
Q_C^{\sigma}(\xi'\mid \xi)
+
\sum_{b\in B_C}\Lambda_C^{\sigma}(b\mid \xi)\rho_C(\xi'\mid b).
\end{equation}
Its row sums are equal to one by construction.

If $\pi_C^{\sigma,\mathrm{book}}$ denotes an invariant law of
$\widetilde Q_C^{\sigma}$, define the internal occupation measure and exit rate by
\[
\mu_C^{\sigma}(\xi,a):=\pi_C^{\sigma,\mathrm{book}}(\xi)\sigma_C(a\mid\xi),
\qquad
\beta_C^{\sigma}(b):=\sum_{(\xi,a)\in\Omega_C}
\mu_C^{\sigma}(\xi,a)\lambda_C(b\mid\xi,a).
\]
The pair is denoted by
\[
\bar\mu_C^{\sigma}=(\mu_C^{\sigma},\beta_C^{\sigma}).
\]


\begin{definition}
\label{def:PC}
The \emph{internal feasible set} of node $C$ is the set of all
$\mu\in\R_+^{\Omega_C}$ for which there exists $\beta\in\R_+^{B_C}$ such that
\begin{align}
\sum_{(\xi,a)\in\Omega_C}\mu(\xi,a)&=1,
\label{eq:norm-PC}
\\
\pi_\mu(\xi')
&=
\sum_{(\xi,a)\in\Omega_C}\mu(\xi,a)P_C^0(\xi'\mid\xi,a)
+
\sum_{b\in B_C}\beta(b)\rho_C(\xi'\mid b)
\qquad (\xi'\in\Xi_C),
\label{eq:internal-balance}
\\
\beta(b)
&=
\sum_{(\xi,a)\in\Omega_C}\mu(\xi,a)\lambda_C(b\mid\xi,a)
\qquad (b\in B_C),
\label{eq:beta-balance}
\end{align}
where
\[
\pi_\mu(\xi):=\sum_{a\in\prod_j A_j(\xi)}\mu(\xi,a).
\]
We denote this set by $\cP_C$.
\end{definition}


\begin{remark}
The restart kernel $\rho_C$ belongs only to the bookkeeping balance equations
\eqref{eq:internal-balance}. It does not describe what the executed block does
after leaving node $C$. In the executed dynamics the live segment ends at the
first cemetery state; the launched block interval is then completed by keeping
that recorded cemetery state in public memory until the next scheduled boundary,
and the global routing update is performed only at that boundary in
Section~\ref{sec:realization}.
\end{remark}

\subsection{The graph theorem for exit fluxes}

Define the linear exit map
\begin{equation}
\label{eq:LC-def}
L_C:\R^{\Omega_C}\to \R^{B_C},
\qquad
(L_C\mu)(b):=
\sum_{(\xi,a)\in\Omega_C}\mu(\xi,a)\lambda_C(b\mid\xi,a).
\end{equation}
The associated restart operator is
\begin{equation}
\label{eq:RC-def}
R_C:\R^{B_C}\to \R^{\Xi_C},
\qquad
(R_C\beta)(\xi'):=\sum_{b\in B_C}\beta(b)\rho_C(\xi'\mid b).
\end{equation}


\begin{proposition}
\label{prop:PC-polytope}
For every node $C$, the set $\cP_C$ is a nonempty compact convex polytope.
Moreover, $\mu\in\cP_C$ if and only if
\begin{align}
\sum_{(\xi,a)}\mu(\xi,a)&=1,
\label{eq:PC-short1}
\\
\pi_\mu &= P_C^0\mu + R_C L_C\mu,
\label{eq:PC-short2}
\end{align}
where $(P_C^0\mu)(\xi'):=\sum_{(\xi,a)}\mu(\xi,a)P_C^0(\xi'\mid\xi,a)$.
\end{proposition}

\begin{proof}
The defining relations in \Cref{def:PC} are finitely many linear equalities and
inequalities in the variables $(\mu,\beta)$. Hence the feasible set in
$\R_+^{\Omega_C}\times\R_+^{B_C}$ is a compact convex polyhedron; compactness
comes from \eqref{eq:norm-PC}. Projecting onto the $\mu$-coordinates shows that
$\cP_C$ is a compact convex polytope.

If $\mu\in\cP_C$, the auxiliary vector $\beta$ is unique by
\eqref{eq:beta-balance}, namely $\beta=L_C\mu$. Substituting this into
\eqref{eq:norm-PC} and \eqref{eq:internal-balance} gives
\eqref{eq:PC-short1}--\eqref{eq:PC-short2}. Conversely, if
\eqref{eq:PC-short1}--\eqref{eq:PC-short2} hold and one sets $\beta=L_C\mu$, then
all three relations from \Cref{def:PC} are satisfied.
\end{proof}


\begin{definition}
\label{def:MCbook}
The \emph{bookkeeping augmented feasible set} of node $C$ is
\[
\cM_C^{\mathrm{book}}
:=
\{(\mu,\beta)\in\cP_C\times\R_+^{B_C}:\beta=L_C\mu\}.
\]
The affine graph map is
\[
J_C:\cP_C\to \cM_C^{\mathrm{book}},
\qquad J_C(\mu)=(\mu,L_C\mu).
\]
\end{definition}

\begin{theorem}[Graph theorem for the bookkeeping node]
\label{thm:graph-theorem}
For every node $C$,
\[
\cM_C^{\mathrm{book}} = J_C(\cP_C).
\]
The map $J_C$ is affine and injective. In particular the exit coordinates are not
independent variables: once the internal part $\mu$ is fixed, the exit mass is
uniquely determined as $L_C\mu$.
\end{theorem}

\begin{proof}
The identity is immediate from \Cref{def:MCbook}. Affineness follows from the
linearity of $L_C$, and injectivity is obvious from the first coordinate.
\end{proof}

\begin{corollary}
\label{cor:no-vp3}
There is no separate compatibility condition between internal occupation and exit
mass. The feasible bookkeeping set is exactly the graph of the linear exit map.
\end{corollary}

\begin{proof}
This is a restatement of \Cref{thm:graph-theorem}.
\end{proof}

\subsection{Actual bookkeeping packages induced by stationary mixed kernels}

\begin{definition}
\label{def:actual-local-package}
For a stationary mixed kernel $\sigma_C\in\Sigma_C$, its \emph{actual bookkeeping
occupation} is the pair $\bar\mu_C^{\sigma}$ induced by an invariant law of the
bookkeeping kernel \eqref{eq:bookkeeping-kernel}. By construction,
$\bar\mu_C^{\sigma}\in \cM_C^{\mathrm{book}}$.
\end{definition}

\begin{proof}
Let $\pi=\pi_C^{\sigma,\mathrm{book}}$ be an invariant law of
$\widetilde Q_C^{\sigma}$. Writing the stationarity equation for
$\widetilde Q_C^{\sigma}$ and expanding \eqref{eq:bookkeeping-kernel} gives
exactly \eqref{eq:norm-PC}--\eqref{eq:beta-balance} with
$\mu=\mu_C^{\sigma}$ and $\beta=\beta_C^{\sigma}$.
\end{proof}

\section{Local average-reward games and Bellman certificates}
\label{sec:local}

\subsection{Local continuation values}

Fix $\eta\in(0,1)$ and a node $C$. Let $x$ be a package of continuation data on the
whole tree. For each boundary state $b\in B_C$ the successor $D=C[b]$ is always a
child node of the enlarged tree. The value
$v_C^x(b)\in[0,d_\eta(C)-1]^N$ is the continuation vector stored at that boundary
coordinate in $x$ and required later to be $\eta$-close to $g_D^x$. If $D$ is an
ordinary child, this is its local gain vector. If $D=T_b$ is a degenerate
terminal child, then $g_D^x=w(D)=w(b)$ exactly and $h_D^x=0$. Thus exits to
degenerate terminal nodes enter the local Bellman equations through the same
frozen continuation coordinates as all other exits. There is no separate
terminal accounting outside the fixed-point system. Throughout this section $x$
is considered fixed.

\subsection{The genuine augmented kernel and the augmented stage payoff}

Fix a node $C$ and a stationary mixed kernel $\sigma_C\in\Sigma_C$. The
\emph{genuine augmented state space} is
\[
\Xi_C^{\mathrm{aug}}:=\Xi_C\sqcup \partial B_C,
\qquad
\partial B_C:=\{\partial_b:b\in B_C\}.
\]
The executed augmented kernel is
\begin{equation}
\label{eq:aug-kernel}
P_C^{\sigma,\mathrm{aug}}(z\mid y)
=
\begin{cases}
Q_C^{\sigma}(\xi'\mid \xi), & y=\xi\in\Xi_C,\ z=\xi'\in\Xi_C,\\[0.3em]
\Lambda_C^{\sigma}(b\mid \xi), & y=\xi\in\Xi_C,\ z=\partial_b,\\[0.3em]
1, & y=z=\partial_b,\\[0.3em]
0, & \text{otherwise.}
\end{cases}
\end{equation}
Thus cemetery states are absorbing. The live part of the executed controller ends
at the first cemetery hit; in a launched scheduled block, the recorded cemetery
state is then carried passively until the block boundary. The absorbing
completion in \eqref{eq:aug-kernel} is used to encode exactly that intrablock
behavior and to make the kernel stochastic.

For a fixed player $i$ and opponents' kernel $\sigma_{-i}$, the stage reward part,
the internal transition part, and the exit part are
\begin{align}
\label{eq:r-sigma}
r_{i,C}^{\sigma_{-i}}(\xi,a_i)
&:=
\sum_{a_{-i}}\sigma_{-i}(a_{-i}\mid\xi)
\,u_i\bigl(\xi,(a_i,a_{-i})\bigr),
\\
\label{eq:Q-sigma}
Q_{i,C}^{\sigma_{-i}}(\xi'\mid \xi,a_i)
&:=
\sum_{a_{-i}}\sigma_{-i}(a_{-i}\mid\xi)
\,P_C^0\bigl(\xi'\mid\xi,(a_i,a_{-i})\bigr),
\\
\label{eq:q-exit-sigma}
\Lambda_{i,C}^{\sigma_{-i}}(b\mid\xi,a_i)
&:=
\sum_{a_{-i}}\sigma_{-i}(a_{-i}\mid\xi)
\,\lambda_C\bigl(b\mid\xi,(a_i,a_{-i})\bigr).
\end{align}
The associated \emph{augmented one-step reward} is
\begin{equation}
\label{eq:augmented-reward}
\widetilde r_{i,C}^{\sigma_{-i},x}(\xi,a_i)
:=
r_{i,C}^{\sigma_{-i}}(\xi,a_i)
+
\sum_{b\in B_C}\Lambda_{i,C}^{\sigma_{-i}}(b\mid\xi,a_i)v_{i,C}^x(b).
\end{equation}
This is exactly the one-step reward relevant for the live first-exit MDP: the
ordinary stage payoff is earned inside $\Xi_C$, and if the next state is the
first cemetery state $\partial_b$, the controller records one copy of the
continuation value $v_{i,C}^x(b)$ at that live exit. When the controller is later
embedded into a launched scheduled block, the remaining scheduled cemetery stages
after that exit are accounted for separately by the full scheduled-block identity
from \Cref{eq:block-cemetery-payoff,eq:block-full-payoff}.

The Bellman operator is therefore
\begin{equation}
\label{eq:Bellman-operator}
(T_{i,C}^{\sigma_{-i},x}h)(\xi)
:=
\max_{a_i\in A_i(\xi)}\Bigl[
 r_{i,C}^{\sigma_{-i}}(\xi,a_i)
 +\sum_{\xi'\in\Xi_C}Q_{i,C}^{\sigma_{-i}}(\xi'\mid\xi,a_i)h(\xi')
 +\sum_{b\in B_C}\Lambda_{i,C}^{\sigma_{-i}}(b\mid\xi,a_i)v_{i,C}^x(b)
 \Bigr].
\end{equation}
Equivalently, this is the Bellman operator of the augmented MDP on
$\Xi_C^{\mathrm{aug}}$ with cemetery biases fixed at zero.

\begin{lemma}
\label{lem:coeff-affine}
For fixed $C$, $i$, and $x$, the maps
\[
\sigma_{-i}\mapsto r_{i,C}^{\sigma_{-i}},
\qquad
\sigma_{-i}\mapsto Q_{i,C}^{\sigma_{-i}},
\qquad
\sigma_{-i}\mapsto \Lambda_{i,C}^{\sigma_{-i}},
\qquad
\sigma_{-i}\mapsto \widetilde r_{i,C}^{\sigma_{-i},x}
\]
are affine. Consequently there exists a finite constant $K_{i,C}$ such that for
all $\sigma_{-i},\tau_{-i}$,
\begin{align}
\|\widetilde r_{i,C}^{\tau_{-i},x}-\widetilde r_{i,C}^{\sigma_{-i},x}\|_\infty
&\le K_{i,C}\|\tau_{-i}-\sigma_{-i}\|_1,
\label{eq:r-lip}
\\
\sup_{\xi,a_i}\|Q_{i,C}^{\tau_{-i}}(\cdot\mid\xi,a_i)-Q_{i,C}^{\sigma_{-i}}(\cdot\mid\xi,a_i)\|_{\mathrm{TV}}
&\le K_{i,C}\|\tau_{-i}-\sigma_{-i}\|_1,
\label{eq:Q-lip}
\\
\sup_{\xi,a_i}\|\Lambda_{i,C}^{\tau_{-i}}(\cdot\mid\xi,a_i)-\Lambda_{i,C}^{\sigma_{-i}}(\cdot\mid\xi,a_i)\|_{1}
&\le K_{i,C}\|\tau_{-i}-\sigma_{-i}\|_1.
\label{eq:Lambda-lip}
\end{align}
\end{lemma}

\begin{proof}
Each coefficient is a finite linear combination of the components of
$\sigma_{-i}(\cdot\mid\xi)$, with coefficients given by the primitive reward,
transition, and continuation data. This proves affineness. The Lipschitz bounds
follow because all underlying arrays are bounded and finite.
\end{proof}

\subsection{Local best responses}

We now formulate the local best-response correspondence. Since the local state and
action sets are finite, every unilateral local problem is a finite average-reward
MDP with communicating internal part and bounded continuation rewards at exits.

\begin{definition}
\label{def:local-BR-set}
For fixed $x$, node $C$, and player $i$, let $\mathfrak B_{i,C}(x)$ be the set of
triples $(\sigma_{i,C},g_{i,C},h_{i,C})$ such that
\begin{enumerate}[label=\textnormal{(BR\arabic*)},leftmargin=2.9em]
\item $\sigma_{i,C}\in \Sigma_{i,C}$;
\item $g_{i,C}\in[0,d_\eta(C)]$ and
$h_{i,C}\in[-B_\eta^0,B_\eta^0]^{\Xi_C}$;
\item $h_{i,C}$ is normalized by
\[
h_{i,C}(\xi_C^\circ)=0;
\]
\item for every $\xi\in\Xi_C$,
\begin{equation}
\label{eq:Bellman-ineq-def}
g_{i,C}+h_{i,C}(\xi)
\ge
r_{i,C}^{\sigma_{-i,C}^x}(\xi,a_i)
+
\sum_{\xi'}Q_{i,C}^{\sigma_{-i,C}^x}(\xi'\mid\xi,a_i)h_{i,C}(\xi')
+
\sum_b \Lambda_{i,C}^{\sigma_{-i,C}^x}(b\mid\xi,a_i)v_{i,C}^x(b)
\end{equation}
for every $a_i\in A_i(\xi)$;
\item equality holds in \eqref{eq:Bellman-ineq-def} for every action $a_i$ in the
support of $\sigma_{i,C}(\cdot\mid\xi)$.
\end{enumerate}
\end{definition}

\begin{proposition}
\label{prop:local-BR}
Assume condition~\textnormal{(a)}. For every fixed $x$, node $C$, and player $i$,
the set $\mathfrak B_{i,C}(x)$ is nonempty, compact, and convex. The
correspondence $x\mapsto \mathfrak B_{i,C}(x)$ has closed graph.
\end{proposition}

\begin{proof}
Fix $x$, $C$, and $i$. The Bellman system
\eqref{eq:Bellman-ineq-def} is exactly the dual optimality system for the finite
average-reward MDP faced by player $i$ against the frozen environment encoded by
$x$; see \Cref{prop:mdp-duality}. Because the frozen continuation vector lies in
$[0,d_\eta(C)-1]^N$ and the stage payoffs lie in $[0,1]$, the augmented one-step
reward in that MDP is bounded by $d_\eta(C)$. Hence there exists an optimal
stationary mixed kernel together with a gain-bias pair satisfying
\eqref{eq:Bellman-ineq-def} and the support equalities, with
$g_{i,C}\in[0,d_\eta(C)]$. Therefore $\mathfrak B_{i,C}(x)$ is nonempty.

Compactness follows because $\Sigma_{i,C}$ is a product of simplices and the gain
and bias coordinates are confined to compact boxes. The defining equalities and
inequalities are closed.

For convexity, condition~\textnormal{(a)} implies that the internal part of the
deviation MDP is communicating on $\Xi_C$. For communicating finite MDPs, the
optimal bias is unique up to an additive constant; after the linear normalization
$h(\xi_C^\circ)=0$, the optimal bias is unique, see
\Cref{prop:bias-unique} and \cite[Chapter~8]{Puterman1994}. The same is true for
the optimal gain. Hence, once $x$ is fixed, there is a unique normalized optimal
pair $(g^*,h^*)$. A stationary mixed kernel is optimal if and only if, at every
state, it assigns mass only to actions attaining equality in the Bellman system
for $(g^*,h^*)$. The set of such kernels is a product of simplices and hence
convex. Thus $\mathfrak B_{i,C}(x)$ is convex.

For the graph property, let $x^m\to x$ and let
$(\sigma_i^m,g_i^m,h_i^m)\in \mathfrak B_{i,C}(x^m)$ converge to
$(\sigma_i,g_i,h_i)$. The coefficient arrays from \Cref{lem:coeff-affine} depend
continuously on $x$, hence passing to the limit in the Bellman equalities and
inequalities shows $(\sigma_i,g_i,h_i)\in\mathfrak B_{i,C}(x)$.
\end{proof}

\subsection{Local equilibrium existence}

\begin{proposition}[Local stationary Nash equilibrium]
\label{prop:local-equilibrium}
Assume condition~\textnormal{(a)}. Fix $x$ and a node $C$. There exists a
stationary mixed kernel $\sigma_C^*\in\Sigma_C$ such that for every player $i$,
$(\sigma_{i,C}^*,g_{i,C}^*,h_{i,C}^*)\in \mathfrak B_{i,C}(x)$ for some
$(g_{i,C}^*,h_{i,C}^*)$. Equivalently, the local average game at node $C$ with
continuation values frozen at $x$ has a stationary Nash equilibrium, and every
player admits a Bellman certificate at that equilibrium.
\end{proposition}

\begin{proof}
Fix the continuation vector $v_C^x(\cdot)$ extracted from $x$. For each player
$i$ and every opponents' kernel
$\sigma_{-i,C}\in\prod_{j\ne i}\Sigma_{j,C}$, let
\[
\BR_{i,C}^x(\sigma_{-i,C})
:=
\{\tau_{i,C}\in\Sigma_{i,C}: \exists g,h\text{ with }
(\tau_{i,C},g,h)\text{ satisfying \eqref{eq:Bellman-ineq-def} against }
\sigma_{-i,C}\text{ and }v_C^x\}.
\]
By the same MDP-duality argument as in \Cref{prop:local-BR}, each value
$\BR_{i,C}^x(\sigma_{-i,C})$ is nonempty, compact, and convex, and the graph of
the playerwise best-response correspondence is closed. Define the product
correspondence on $\Sigma_C$ by
\[
\BR_C^x(\sigma_C):=\prod_{i\in N}\BR_{i,C}^x(\sigma_{-i,C}).
\]
Its values are therefore nonempty, compact, and convex, and its graph is closed.
Since $\Sigma_C$ is a compact convex product of simplices, Kakutani's theorem
\cite{Kakutani1941} yields a fixed point $\sigma_C^*\in\BR_C^x(\sigma_C^*)$. For
each player $i$, choose a Bellman certificate $(g_{i,C}^*,h_{i,C}^*)$ associated
with the best-response relation at that fixed point. This is exactly the required
local stationary Nash package.
\end{proof}

\begin{remark}
This proposition is the correct multiplayer replacement for the v4 appendix, which
contained only one-player LP duality. One-player LP duality is still needed, but
only to identify each player's best-response set. Existence of a simultaneous
local Nash package requires the fixed-point step above.
\end{remark}

\section{The global correspondence with frozen continuation values}
\label{sec:global}

\subsection{Ambient package space}

A global package contains, at each node and for each player, a stationary mixed
kernel and a Bellman certificate, together with nodewise continuation values.
There is \emph{no} self-consistency requirement in the ambient space.

\begin{definition}
\label{def:Aeta}
For fixed $\eta\in(0,1)$, the ambient package space $\cA_\eta$ consists of all
families
\[
x=\Bigl((\sigma_{i,C},g_{i,C},h_{i,C})_{i\in N},\ (v_C(b))_{b\in B_C}\Bigr)_{C\in\cT_\eta}
\]
such that:
\begin{enumerate}[label=\textnormal{(A\arabic*)},leftmargin=2.8em]
\item $\sigma_{i,C}\in \Sigma_{i,C}$ for all $i,C$;
\item $g_{i,C}\in[0,d_\eta(C)]$ for all $i,C$;
\item $h_{i,C}\in[-B_\eta^0,B_\eta^0]^{\Xi_C}$ and
$h_{i,C}(\xi_C^\circ)=0$ for all $i,C$;
\item $v_C(b)\in[0,d_\eta(C)-1]^N$ for all $C$ and $b\in B_C$.
\end{enumerate}
\end{definition}

\begin{proposition}
\label{prop:Aeta-compact}
For every $\eta\in(0,1)$, the set $\cA_\eta$ is compact and convex.
\end{proposition}

\begin{proof}
Each $\Sigma_{i,C}$ is a product of simplices, hence compact and convex. The gain
coordinates lie in the depth-dependent intervals $[0,d_\eta(C)]$, the bias
coordinates lie in a compact box intersected with the linear normalization
hyperplane $h(\xi_C^\circ)=0$, and the continuation values lie in the
depth-dependent cubes $[0,d_\eta(C)-1]^N$. Because the tree is finite,
$\cA_\eta$ is a finite product of compact convex sets.
\end{proof}

\subsection{Global best response}

The key point is that continuation values are frozen from the reference package
$x$. The response package $y$ is allowed to differ from $x$.

\begin{definition}
\label{def:global-BR}
For $x\in\cA_\eta$, define $\BR_\eta(x)$ to be the set of all packages
$y\in\cA_\eta$ such that:
\begin{enumerate}[label=\textnormal{(G\arabic*)},leftmargin=2.8em]
\item for every node $C$ and every player $i$,
\[
(\sigma_{i,C}^y,g_{i,C}^y,h_{i,C}^y)\in \mathfrak B_{i,C}(x);
\]
\item whenever $b\in B_C$ and $D=C[b]$, one has
\begin{equation}
\label{eq:frozen-continuation}
\|v_C^y(b)-g_D^x\|_\infty\le \eta,
\end{equation}
where $g_D^x=(g_{i,D}^x)_{i\in N}$.
\end{enumerate}
\end{definition}

\begin{remark}
The response package $y$ is assembled against \emph{frozen} continuation values and
frozen opponents from $x$. There is no circularity here. One does not ask $y$ to
be self-consistent while defining $\BR_\eta(x)$; that happens only at a fixed
point. This is exactly the continuation repair already made in v5 and retained in
v6.
\end{remark}

\begin{theorem}[Global Kakutani fixed point]
\label{thm:kakutani-global}
Assume condition~\textnormal{(a)}. For every $\eta\in(0,1)$, the correspondence
$\BR_\eta:\cA_\eta\rightrightarrows\cA_\eta$ has nonempty compact convex values and
closed graph. Consequently it has a fixed point $x^*\in\cA_\eta$.
\end{theorem}

\begin{proof}
By \Cref{prop:Aeta-compact}, the domain $\cA_\eta$ is compact and convex.

Fix $x\in\cA_\eta$. For every node $C$ and player $i$, the set
$\mathfrak B_{i,C}(x)$ is nonempty, compact, and convex by
\Cref{prop:local-BR}. The continuation constraints
\eqref{eq:frozen-continuation} are closed convex constraints. Therefore
$\BR_\eta(x)$ is a finite product of nonempty compact convex sets, hence itself
nonempty, compact, and convex.

For the graph property, let $x^m\to x$ and $y^m\to y$ with
$y^m\in\BR_\eta(x^m)$ for all $m$. For every node $C$ and player $i$ we have
$(\sigma_{i,C}^{y^m},g_{i,C}^{y^m},h_{i,C}^{y^m})\in\mathfrak B_{i,C}(x^m)$. By
the closed-graph property from \Cref{prop:local-BR}, the limit belongs to
$\mathfrak B_{i,C}(x)$. Passing to the limit in the continuation inequalities gives
\eqref{eq:frozen-continuation} for $y$ against $x$. Hence $y\in\BR_\eta(x)$, so
$\BR_\eta$ has closed graph.

Closed graph plus compact values on a compact domain imply upper
hemicontinuity. Kakutani's theorem \cite{Kakutani1941} yields a fixed point.
\end{proof}

\begin{corollary}
\label{cor:local-nash-at-fixed-point}
If $x^*\in\BR_\eta(x^*)$, then for every node $C$ the stationary mixed kernel
$\sigma_C^*:=(\sigma_{i,C}^*)_{i\in N}$ is a local stationary Nash equilibrium of
the node game with continuation values $v_C^{x^*}(\cdot)$, and each player has a
Bellman certificate $(g_{i,C}^*,h_{i,C}^*)$.
\end{corollary}

\begin{proof}
At a fixed point,
$(\sigma_{i,C}^*,g_{i,C}^*,h_{i,C}^*)\in\mathfrak B_{i,C}(x^*)$ for every $i,C$.
Thus each player's stationary mixed kernel is a best response to the others inside
node $C$, against the continuation values carried by $x^*$. That is exactly the
local stationary Nash property.
\end{proof}

\section{Local controllers and global realization}
\label{sec:realization}


\subsection{The node controller, live first exits, and launched blocks}

Fix a fixed point $x^*\in\BR_\eta(x^*)$. For each node $C$, write
\[
\sigma_C^*:=(\sigma_{i,C}^*)_{i\in N},
\qquad
\bar\mu_C^*:=(\mu_C^{\sigma_C^*},\beta_C^{\sigma_C^*}).
\]
The local controller for node $C$ is the first-exit controller
$\mathcal R_{C,L}^{\sigma_C^*}$ supplied by \Cref{ass:controller-input}. When the
controller is launched with cap $L$, it evolves on
$\Xi_C^{\mathrm{aug}}=\Xi_C\sqcup\partial B_C$ until the live stopping time
$\tau_{C,L}\le L$. This live first-exit time governs the local renewal-reward
estimate. At the level of the global strategy, however, the launched block
occupies the full scheduled interval of length $L$; after the first cemetery
hit, if any, the public memory simply records the unique label and waits until
the scheduled boundary.

For a launched block $B$ in node $C$, let $|B|:=L(B)$ denote its scheduled
length and let $\tau(B)\le |B|$ denote its live duration. Let $N_B(\xi,a)$ be the
number of live stages in $B$ at which $(X_t,A_t)=(\xi,a)$, and let $I_B(b)$ be the
indicator that the live segment of $B$ exits at $\partial_b$. The empirical
live-time rates are
\[
\widehat\mu_B^{\mathrm{rate}}(\xi,a):=\frac{N_B(\xi,a)}{\tau(B)},
\qquad
\widehat\beta_B(b):=\frac{I_B(b)}{\tau(B)}.
\]
For any evaluation profile $\varsigma$ on the launched block $B$, the total
augmented live reward is
\begin{equation}
\label{eq:aug-block-payoff}
\widetilde U_i(B;\varsigma)
:=
\sum_{t\in B^{\mathrm{live}}} u_i^t(\varsigma)
+
\sum_{b\in B_C}I_B(b)\,v_{i,C}^{x^*}(b).
\end{equation}
Because \eqref{eq:aug-block-payoff} already books one copy of the continuation
rate at the live exit, the remaining cemetery completion of the scheduled block
is
\begin{equation}
\label{eq:block-cemetery-payoff}
U_i^{\mathrm{cem}}(B)
:=
\sum_{b\in B_C}I_B(b)\,\bigl(|B|-\tau(B)-1\bigr)_+\,v_{i,C}^{x^*}(b).
\end{equation}
The \emph{full scheduled-block payoff} is therefore
\begin{equation}
\label{eq:block-full-payoff}
U_i^{\mathrm{full}}(B;\varsigma)
:=
\widetilde U_i(B;\varsigma)+U_i^{\mathrm{cem}}(B).
\end{equation}
Equivalently, $U_i^{\mathrm{full}}(B;\varsigma)$ is the payoff over all scheduled
stages of $B$: the live phase contributes the ordinary stage payoffs, and after a
cemetery hit the remaining scheduled stages contribute the fixed continuation rate
attached to the public exit label.

If the live segment reaches its cap without a cemetery hit, then $I_B\equiv 0$ and
\[
U_i^{\mathrm{full}}(B;\varsigma)
=
\widetilde U_i(B;\varsigma)
=
\sum_{t\in B^{\mathrm{live}}}u_i^t(\varsigma).
\]
If $C=T$ is degenerate terminal, then $B_C=\varnothing$, so
\[
U_i^{\mathrm{full}}(B;\varsigma)
=
\widetilde U_i(B;\varsigma)
=
w_i(T)\,|B|,
\]
because $\tau(B)=|B|$ in a degenerate terminal node. Thus the same notation
covers ordinary and degenerate nodes uniformly.

\begin{theorem}[Local controller lemma]

\label{thm:local-controller}
Assume \Cref{ass:controller-input}. Fix a node $C$ and the fixed-point kernel
$\sigma_C^*$. Then there exists a constant $K_C<\infty$ such that for every cap
$L\ge 1$, every entry phase-state, and every player $i$,
\begin{equation}
\label{eq:local-controller-occ}
\E\bigl[\|(\widehat\mu_{C,L}^{\mathrm{rate}},\widehat\beta_{C,L})-\bar\mu_C^*\|_1\bigr]
\le \frac{K_C}{\sqrt L},
\end{equation}
and
\begin{equation}
\label{eq:local-controller-payoff}
\left|
\frac{\E[\widetilde U_{i,C,L}]}{\E[\tau_{C,L}]}
-
g_{i,C}^*
\right|
\le \frac{K_C}{\sqrt L}.
\end{equation}
Consequently, for every $\delta>0$ there exists $L_C(\delta)$ such that the block
controller is $\delta$-accurate in the sense of
\eqref{eq:local-controller-occ}--\eqref{eq:local-controller-payoff} whenever the
cap $L$ satisfies $L\ge L_C(\delta)$.
\end{theorem}

\begin{proof}
The occupation estimate \eqref{eq:local-controller-occ} is exactly the first-exit
realization estimate from \Cref{ass:controller-input}, with
$K_C:=K_C(\sigma_C^*)$.

Define the bounded linear reward-rate functional
\[
\Phi_{i,C}(\mu,\beta)
:=
\sum_{(\xi,a)\in\Omega_C}\mu(\xi,a)u_i(\xi,a)
+
\sum_{b\in B_C}\beta(b)v_{i,C}^{x^*}(b).
\]
By \eqref{eq:controller-input-renewal},
\[
\left|
\frac{\E[\widetilde U_{i,C,L}]}{\E[\tau_{C,L}]}
-
\Phi_{i,C}(\bar\mu_C^*)
\right|
\le \frac{K_C'}{\sqrt L}.
\]

It remains to identify the target. Integrating the Bellman equalities for actions
in the support of $\sigma_{i,C}^*(\cdot\mid\xi)$ against the bookkeeping rate
package $\bar\mu_C^*=(\mu_C^*,\beta_C^*)$ and using
\eqref{eq:internal-balance}--\eqref{eq:beta-balance} yields
\[
g_{i,C}^*
=
\sum_{(\xi,a)}\mu_C^*(\xi,a)u_i(\xi,a)
+
\sum_{b\in B_C}\beta_C^*(b)v_{i,C}^{x^*}(b)
-
\sum_{\xi'\in\Xi_C}(R_C\beta_C^*)(\xi')h_{i,C}^*(\xi').
\]
Because the bookkeeping restart is fixed at the reference state,
$\rho_C(\cdot\mid b)=\delta_{\xi_C^\circ}$ for every $b\in B_C$, one has
\[
(R_C\beta_C^*)(\xi')
=
\Bigl(\sum_{b\in B_C}\beta_C^*(b)\Bigr)\delta_{\xi_C^\circ}(\xi').
\]
Hence the restart-bias term vanishes:
\[
\sum_{\xi'\in\Xi_C}(R_C\beta_C^*)(\xi')h_{i,C}^*(\xi')
=
\Bigl(\sum_{b\in B_C}\beta_C^*(b)\Bigr)h_{i,C}^*(\xi_C^\circ)
=
0,
\]
because $h_{i,C}^*(\xi_C^\circ)=0$ by normalization. Therefore
\[
g_{i,C}^*
=
\sum_{(\xi,a)}\mu_C^*(\xi,a)u_i(\xi,a)
+
\sum_{b\in B_C}\beta_C^*(b)v_{i,C}^{x^*}(b)
=
\Phi_{i,C}(\bar\mu_C^*).
\]
Combining the two displays proves \eqref{eq:local-controller-payoff} after
absorbing constants into $K_C$. This is precisely the renewal-reward identity for
the live first-exit segment: the correct normalization uses the actual first-exit
time $\tau_{C,L}$, not the cap $L$. The remaining scheduled cemetery stages of a
launched block are added later through the full scheduled-block identity
\eqref{eq:block-full-payoff}.
\end{proof}

\subsection{Frozen superexponential schedule}


\begin{definition}
A sequence $(M_r)_{r\ge 1}$ of positive integers is a
\emph{superexponential schedule} if $M_{r+1}\ge M_r^2$ for all $r$. Its
\emph{freezing at level $R$} is the sequence $(M_r^{(R)})_{r\ge 1}$ defined by
\[
M_r^{(R)}=
\begin{cases}
M_r, & r<R,\\
M_R, & r\ge R.
\end{cases}
\]
We write $M_*:=M_R$ for the tail block length.
\end{definition}

\begin{lemma}
\label{lem:frozen-memory}
A frozen superexponential schedule uses only finite public memory.
\end{lemma}

\begin{proof}
Only the finitely many lengths $M_1,\dots,M_R$ appear. To implement the schedule
one stores the current node, the current position inside the current block, the
current local memory state of the node controller, and the block index truncated at
$R$. All of these coordinates range over finite sets.
\end{proof}

\begin{definition}[Scheduled block partition]
\label{def:scheduled-block-partition}
Fix a frozen superexponential schedule and a public routing automaton. Let
$t_1:=1$. At each launch time $t_k$, the public memory determines a current node
$C_k$ and a cap $L_k$; the automaton launches the controller
$\mathcal R_{C_k,L_k}^{\sigma_{C_k}^*}$ and defines the $k$th \emph{scheduled
block} by
\[
B_k:=[t_k,t_k+L_k).
\]
The next launch time is $t_{k+1}:=t_k+L_k$. Hence the triple $(t_k,C_k,L_k)$ is
fixed at launch from public data alone. The live first-exit time inside $B_k$ is
a random variable $\tau(B_k)\le L_k$, but it does not alter the boundary
$t_k+L_k$ of the launched block.
\end{definition}

\subsection{Public routing and realization}

Recall from \Cref{rem:tree-depth} that $D_\eta<\infty$ is the maximal number of
node layers on a root-to-leaf path of the finite universal tree $\cT_\eta$.

\begin{proposition}[Public routing]
\label{prop:public-routing}
Fix a fixed point $x^*$ and a frozen superexponential schedule. There exists a
public finite-memory profile $\sigma_{\eta,\delta,M_*}$ with the following
properties.
\begin{enumerate}[label=\textnormal{(R\arabic*)},leftmargin=2.8em]
\item At each launch time $t_k$ the public routing automaton reads the current
public memory, chooses a node $C_k$ and the next cap $L_k$ from the frozen
schedule, and launches the controller $\mathcal R_{C_k,L_k}^{\sigma_{C_k}^*}$.
The resulting block is the scheduled interval $B_k=[t_k,t_k+L_k)$ from
\Cref{def:scheduled-block-partition}.
\item Once $B_k$ is launched, its right boundary $t_k+L_k$ is fixed. Inside $B_k$
the live path follows the controller until its first cemetery hit time
$\tau(B_k)\le L_k$, if such a hit occurs, and otherwise for all $L_k$ stages. If
a cemetery state $\partial_b$ is hit before the scheduled boundary, the unique
label $b$ is recorded, the public memory remains in that absorbed intrablock
state until $t_k+L_k$, and each remaining scheduled stage of $B_k$ contributes
the fixed continuation rate $v_{i,C_k}^{x^*}(b)$ to player $i$.
\item At the scheduled boundary $t_k+L_k$, the next block starts immediately. If
label $b$ was recorded in $B_k$, the next block is launched in the successor node
$D=C_k[b]$. This successor may be an ordinary child or a degenerate terminal
child $T_b$. If $D=T_b$, then every subsequent block is played in $T_b$, no
boundary label is ever emitted again, and each such block simply stays at the
unique internal state of $T_b$ for its full cap while earning $w(T_b)=w(b)$ per
stage. If no label is recorded in $B_k$, the next block starts in the same node
$C_k$.
\item Because routing on recorded cemetery hits always moves to a strict child and
degenerate terminal nodes have no exits, every play path contains at most
$D_\eta$ recorded cemetery exits.
\item The public memory stores the current node, the current cap index, the
current position inside the current scheduled block, the current local controller
state on the live segment, and the unique recorded boundary label, if one has
already occurred. The launch times, block boundaries, and cemetery completions are
therefore publicly observable and deterministic conditional on that memory.
\end{enumerate}
\end{proposition}

\begin{proof}
Item~(R1) is the frozen schedule together with the controller supplied by
\Cref{ass:controller-input}. Item~(R2) combines the first-exit realization with
the convention that, after the unique cemetery hit, the public memory simply
stores the absorbed cemetery state until the already announced block boundary and
pays the fixed continuation rate attached to the recorded public label on every
remaining scheduled stage. Because the first cemetery hit is unique, at most one
boundary label can be recorded.

For (R3), the successor map $b\mapsto C[b]$ belongs to the node data, so once a
label $b$ has been recorded the next routing decision is deterministic at the
scheduled boundary: the next block starts in the child node $D=C[b]$. If $D$ is
degenerate terminal, then its controller is the trivial one-state controller from
the remark after \Cref{ass:controller-input}, so all subsequent blocks remain
there. If no label is recorded, the controller stays in the same node. The bound
by $D_\eta$ follows from finiteness of the tree and the fact that every
cemetery-routing move to a child strictly decreases the remaining depth. Finite
memory comes from \Cref{lem:frozen-memory}, and all relevant quantities are
publicly observable.
\end{proof}

\begin{remark}[Strategy-independent launched blocks]
\label{rem:strategy-independent-blocks}
The launched block partition is determined by the public routing automaton and
the frozen cap sequence. At launch time $t_k$ the automaton publicly fixes the
triple $(t_k,C_k,L_k)$, hence the interval $B_k=[t_k,t_k+L_k)$ is fixed before
any intrablock action is chosen. A unilateral deviation may change the live
first-exit time $\tau(B_k)$ or the recorded boundary label, and thus the
successor node of the \emph{next} block, but it cannot change the current block
interval itself. Therefore both the compliant and deviating evaluations on block
$k$ are carried out on the same launched interval $B_k$, and the cemetery
completion from \Cref{eq:block-cemetery-payoff} is attached to that launched block
record. The only part of block~$k$ that enters the incentive comparison is the
live first-exit segment.
\end{remark}


\begin{theorem}[Realization theorem]
\label{thm:realization}
Assume condition~\textnormal{(a)} and \Cref{ass:controller-input}. Fix
$\eta\in(0,1)$ and a fixed point $x^*\in\BR_\eta(x^*)$. Let
$\sigma_{\eta,\delta,M_*}$ be the public profile obtained from
\Cref{prop:public-routing} by freezing a superexponential schedule at level $R$.
Then there exist constants $C_\eta,K_\eta<\infty$ such that:
\begin{enumerate}[label=\textnormal{(Q\arabic*)},leftmargin=2.8em]
\item if a complete scheduled block $B$ is played in node $C$ and its cap
satisfies $|B|=L(B)\ge M_*$, then
\begin{equation}
\label{eq:block-occupation-realization}
\E\bigl[\|(\widehat\mu_B^{\mathrm{rate}},\widehat\beta_B)-\bar\mu_C^*\|_1
\mid \cF_{\mathrm{in}(B)}\bigr]
\le \delta;
\end{equation}
\item for every player $i$ and every complete scheduled block $B$ played in node
$C$ whose cap satisfies $|B|=L(B)\ge M_*$,
\begin{equation}
\label{eq:block-full-payoff-realization}
\E\bigl[U_i^{\mathrm{full}}(B;\sigma_{\eta,\delta,M_*})\mid \cF_{\mathrm{in}(B)}\bigr]
\ge
\bigl(g_{i,C}^*-C_\eta\delta\bigr)\,\E\bigl[\tau(B)\mid \cF_{\mathrm{in}(B)}\bigr]
+
\E\bigl[U_i^{\mathrm{cem}}(B)\mid \cF_{\mathrm{in}(B)}\bigr];
\end{equation}
\item for every horizon $T$,
\begin{equation}
\label{eq:realization-full-tail-bound}
\left|
\gamma_i^T(s,\sigma_{\eta,\delta,M_*})
-
\frac1T\E\left[
\sum_{B\subseteq [1,T]}
U_i^{\mathrm{full}}(B;\sigma_{\eta,\delta,M_*})
\right]
\right|
\le \frac{K_\eta}{T},
\end{equation}
where the sum is over complete scheduled blocks contained in $[1,T]$. The
constant $K_\eta$ absorbs the initial and final incomplete fragments.
\end{enumerate}
\end{theorem}

\begin{proof}
Item~(Q1) is \Cref{thm:local-controller} at the chosen tail scale, conditioned on
the entry state of the launched block.

For (Q2), \Cref{thm:local-controller} gives
\[
\E\bigl[\widetilde U_i(B;\sigma_{\eta,\delta,M_*})\mid \cF_{\mathrm{in}(B)}\bigr]
\ge
\bigl(g_{i,C}^*-C_\eta\delta\bigr)\,\E\bigl[\tau(B)\mid \cF_{\mathrm{in}(B)}\bigr]
\]
after enlarging $C_\eta$ uniformly over the finite tree. Adding the cemetery
completion from \eqref{eq:block-cemetery-payoff} and using
\eqref{eq:block-full-payoff} yields
\eqref{eq:block-full-payoff-realization}.

For (Q3), decompose the horizon into the complete scheduled blocks contained in
$[1,T]$ together with the initial and final incomplete fragments. By
\eqref{eq:block-full-payoff}, each complete scheduled block contributes exactly
its raw payoff over all scheduled stages in that interval: the live augmented
reward covers the live segment and the cemetery completion covers the remaining
scheduled cemetery stages. Hence the only discrepancy between the horizon-$T$
average payoff and the normalized sum of complete-block full payoffs comes from
the two incomplete fragments, whose total expected contribution is bounded by a
finite constant depending only on the frozen schedule and the finite tree object.
Absorb that constant into $K_\eta$ to obtain
\eqref{eq:realization-full-tail-bound}.
\end{proof}

\section{Condition \texorpdfstring{$(a)$}{(a)}, bias bounds, and the proof of the main theorem}
\label{sec:proof-main}

\subsection{Condition \texorpdfstring{$(a)$}{(a)} in primitive data}

We now formulate the nodewise irreducibility hypothesis directly from the genuine
augmented transition data.

\begin{condition}[Robust nodewise irreducibility]
\label{cond:a}

For every $\eta\in(0,1)$, every node $C\in\cT_\eta$, every player $i\in N$, every
statewise mixed kernel of the other players
$\sigma_{-i}\in\prod_{j\ne i}\Sigma_{j,C}$, and every pure action selection
$a_i(\cdot)$ of player $i$, the augmented kernel
\[
P_{i,C}^{\sigma_{-i},a_i,\mathrm{aug}}(z\mid y)
\]
on $\Xi_C^{\mathrm{aug}}=\Xi_C\sqcup\partial B_C$, defined by
\[
P_{i,C}^{\sigma_{-i},a_i,\mathrm{aug}}(z\mid y)
=
\begin{cases}
\displaystyle
\sum_{a_{-i}}\sigma_{-i}(a_{-i}\mid\xi)
P_C^0\bigl(\xi'\mid\xi,(a_i(\xi),a_{-i})\bigr),
& y=\xi\in\Xi_C,\ z=\xi'\in\Xi_C,\\[0.7em]
\displaystyle
\sum_{a_{-i}}\sigma_{-i}(a_{-i}\mid\xi)
\lambda_C\bigl(b\mid\xi,(a_i(\xi),a_{-i})\bigr),
& y=\xi\in\Xi_C,\ z=\partial_b,\\[0.7em]
1, & y=z=\partial_b,\\
0, & \text{otherwise,}
\end{cases}
\]
has the property that its restriction to the internal states remains irreducible
before absorption: for every $\xi,\zeta\in\Xi_C$ there exists
$0\le n\le |\Xi_C|-1$ with
\[
\bigl(P_{i,C}^{\sigma_{-i},a_i,\mathrm{aug}}\bigr)^n(\zeta\mid\xi)>0.
\]
\end{condition}

\begin{remark}
Condition~\textnormal{(a)} has a direct operational meaning: no single player can,
by choosing actions state by state while the others keep their local kernels,
create a noncommunicating internal class inside a metastable node before the block
is absorbed at a cemetery state.
\end{remark}

\begin{example}
\label{ex:cond-a-trivial}
Suppose that for every node $C$, every phase-state $\xi\in\Xi_C$, and every full
action profile $a\in\prod_j A_j(\xi)$, the internal transition kernel
$P_C^0(\cdot\mid\xi,a)$ belongs to an irreducible family whose directed support
graph is the same strongly connected graph on $\Xi_C$. Then every convex mixture
of those kernels still gives positive probability to each support edge, and hence
every augmented kernel from \Cref{cond:a} can reach any internal state from any
other before absorption. Therefore condition~\textnormal{(a)} holds.
\end{example}

\subsection{A uniform irreducibility modulus}

For fixed $\eta$, define
\begin{equation}
\label{eq:kappa-eta}
\kappa_\eta
:=
\min_{C\in\cT_\eta}
\min_{i\in N}
\inf_{\sigma_{-i}\in\prod_{j\ne i}\Sigma_{j,C}}
\min_{a_i(\cdot)}
\min_{\xi,\zeta\in\Xi_C}
\max_{0\le n\le |\Xi_C|-1}
\Bigl(P_{i,C}^{\sigma_{-i},a_i,\mathrm{aug}}\Bigr)^n(\zeta\mid\xi).
\end{equation}

\begin{lemma}
\label{lem:kappa-positive}
Assume condition~\textnormal{(a)}. Then $\kappa_\eta>0$ for every $\eta\in(0,1)$.
\end{lemma}

\begin{proof}
Fix $C$, $i$, and a pure action selection $a_i(\cdot)$. By
condition~\textnormal{(a)}, every kernel
$P_{i,C}^{\sigma_{-i},a_i,\mathrm{aug}}$ has strictly positive internal
reachability between any two internal states in at most $|\Xi_C|-1$ steps. Hence
the displayed quantity in \eqref{eq:kappa-eta} is strictly positive for each fixed
$\sigma_{-i}$.

The map
$\sigma_{-i}\mapsto P_{i,C}^{\sigma_{-i},a_i,\mathrm{aug}}$ is continuous by
\Cref{lem:coeff-affine}, and the compact domain
$\prod_{j\ne i}\Sigma_{j,C}$ is a finite product of simplices. Therefore the
minimum over that domain is attained and remains strictly positive. Finally there
are only finitely many nodes, players, and pure action selections, so the overall
minimum is strictly positive.
\end{proof}

\subsection{Bias bound}


\begin{lemma}[Hitting the reference state or absorption]
\label{lem:hitting-time}
Let $X$ be a finite set, let $\partial$ be a finite absorbing set, and let $P$ be a
Markov kernel on $X\sqcup\partial$ such that for every $x,y\in X$ there exists
$0\le n\le |X|-1$ with $P^n(y\mid x)>0$. Define
\[
\kappa(P):=\min_{x,y\in X}\max_{0\le n\le |X|-1}P^n(y\mid x).
\]
Then for every $x,y\in X$,
\[
\E_x[\tau_{A_y}]\le \frac{|X|-1}{\kappa(P)},
\qquad
A_y:=\{y\}\cup \partial,
\qquad
\tau_{A_y}:=\inf\{t\ge 0:X_t\in A_y\}.
\]
\end{lemma}

\begin{proof}
If $|X|=1$, then $A_y=X\sqcup\partial$ and $\tau_{A_y}=0$, so the claim is
immediate. Assume henceforth that $|X|\ge 2$ and set $m:=|X|-1$. For each pair
$(x,y)$ choose
$n(x,y)\in\{0,\dots,m\}$ such that
\[
P^{n(x,y)}(y\mid x)\ge \kappa(P).
\]
This is possible by the definition of $\kappa(P)$. Since $n(x,y)\le m$,
\[
\Pb_x(\tau_{A_y}\le m)\ge \Pb_x(X_{n(x,y)}=y)\ge \kappa(P).
\]
Indeed the event $\{X_{n(x,y)}=y\}$ already excludes prior absorption when
$n(x,y)\ge 1$ because all states in $\partial$ are absorbing, and when
$n(x,y)=0$ it simply means $x=y$, in which case $\tau_{A_y}=0$. Therefore
\[
\Pb_x(\tau_{A_y}>m)\le 1-\kappa(P).
\]
Applying the Markov property at times $m,2m,3m,\dots$ on the event
$\{\tau_{A_y}>km\}$, where the chain is still in $X$, gives
\[
\Pb_x(\tau_{A_y}>(k+1)m)\le (1-\kappa(P))\Pb_x(\tau_{A_y}>km)
\qquad (k\ge 0),
\]
hence
\[
\Pb_x(\tau_{A_y}>km)\le (1-\kappa(P))^k.
\]
Therefore
\[
\E_x[\tau_{A_y}]
=
\sum_{t\ge 0}\Pb_x(\tau_{A_y}>t)
\le
m\sum_{k\ge 0}\Pb_x(\tau_{A_y}>km)
\le
m\sum_{k\ge 0}(1-\kappa(P))^k
=
\frac{m}{\kappa(P)}.
\]
\end{proof}


\begin{proposition}[Uniform bias bound]
\label{prop:bias-span}
Assume condition~\textnormal{(a)}. Let $x^*\in\BR_\eta(x^*)$ be a fixed point and
let $(g_{i,C}^*,h_{i,C}^*)$ be the Bellman certificate of player $i$ in node $C$,
normalized by $h_{i,C}^*(\xi_C^\circ)=0$. Then
\[
\|h_{i,C}^*\|_\infty\le
H_\eta:=D_\eta\left(1+\frac{\max_D|\Xi_D|-1}{\kappa_\eta}\right).
\]
In particular,
\[
\spn(h_{i,C}^*)\le 2H_\eta.
\]
\end{proposition}

\begin{proof}
Fix $C$ and $i$. If $C$ is degenerate terminal, then
$g_{i,C}^*=w_i(C)$ and $h_{i,C}^*\equiv 0$ by construction, so the claim is
immediate. Assume henceforth that $C$ is ordinary. Let $a_i^*(\cdot)$ be a
measurable selector choosing, in each state, an action where equality holds in
the Bellman system. Consider the genuine augmented kernel
$P_{i,C}^{\sigma_{-i,C}^*,a_i^*,\mathrm{aug}}$ on
$\Xi_C^{\mathrm{aug}}$. Let
\[
A_C^\circ:=\{\xi_C^\circ\}\cup\partial B_C,
\qquad
\tau^\circ:=\inf\{t\ge 0:X_t\in A_C^\circ\}.
\]
By \Cref{lem:kappa-positive,lem:hitting-time},
\[
\E_\xi[\tau^\circ]\le \frac{|\Xi_C|-1}{\kappa_\eta}
\qquad (\xi\in\Xi_C).
\]

Along the selected policy $a_i^*(\cdot)$, the Bellman equalities read
\[
g_{i,C}^*+h_{i,C}^*(\xi)
=
r_{i,C}^{\sigma_{-i,C}^*}(\xi,a_i^*(\xi))
+
\sum_{\xi'}Q_{i,C}^{\sigma_{-i,C}^*}(\xi'\mid\xi,a_i^*(\xi))h_{i,C}^*(\xi')
+
\sum_b\Lambda_{i,C}^{\sigma_{-i,C}^*}(b\mid\xi,a_i^*(\xi))v_{i,C}^{x^*}(b).
\]
Stopping this identity at $\tau^\circ$ and using $h_{i,C}^*(\xi_C^\circ)=0$ and
the cemetery convention $h_{i,C}^*(\partial_b)=0$ gives the standard relative-value
representation
\[
h_{i,C}^*(\xi)
=
\E_\xi\!\left[
\sum_{t=0}^{\tau^\circ-1}\bigl(u_i^t-g_{i,C}^*\bigr)
+
\sum_{b\in B_C}\1_{\{X_{\tau^\circ}=\partial_b\}}\,v_{i,C}^{x^*}(b)
\right].
\]
Since $u_i^t\in[0,1]$, $g_{i,C}^*\in[0,d_\eta(C)]$, and
$v_{i,C}^{x^*}(b)\in[0,d_\eta(C)-1]$, the absolute value of the last display is
bounded by
\[
\begin{aligned}
d_\eta(C)\,\E_\xi[\tau^\circ] + d_\eta(C)-1
&\le
d_\eta(C)\bigl(\E_\xi[\tau^\circ]+1\bigr)
\\
&\le
D_\eta\left(1+\frac{|\Xi_C|-1}{\kappa_\eta}\right)
\\
&\le
D_\eta\left(1+\frac{\max_D|\Xi_D|-1}{\kappa_\eta}\right)
=
H_\eta.
\end{aligned}
\]
This proves the sup-norm bound. The span bound is immediate.
\end{proof}

\subsection{Deviation-value Lipschitz bound}

\begin{lemma}[Coefficient-level Bellman transfer]
\label{lem:coefficient-transfer}
Let $r,Q$ and $r',Q'$ be two finite average-reward MDP coefficient systems on the
same state-action graph, and let $(g,h)$ satisfy
\[
g+h(x)\ge r(x,a)+\sum_y Q(y\mid x,a)h(y)
\qquad\text{for all }(x,a).
\]
Then
\[
g+h(x)
\ge
r'(x,a)+\sum_y Q'(y\mid x,a)h(y)
-\Bigl(\|r'-r\|_\infty + \spn(h)\sup_{x,a}\|Q'(\cdot\mid x,a)-Q(\cdot\mid x,a)\|_{\mathrm{TV}}\Bigr)
\]
for all $(x,a)$. In particular the perturbation constant is governed by
$1+\spn(h)$, not merely by $\spn(h)$.
\end{lemma}

\begin{proof}
Fix $(x,a)$. Write
\begin{align*}
&r'(x,a)+\sum_y Q'(y\mid x,a)h(y)
-
\Bigl(r(x,a)+\sum_y Q(y\mid x,a)h(y)\Bigr)
\\
&= \bigl(r'(x,a)-r(x,a)\bigr)
+
\sum_y\bigl(Q'(y\mid x,a)-Q(y\mid x,a)\bigr)h(y).
\end{align*}
The first term is bounded by $\|r'-r\|_\infty$. For the second term, subtract the
minimum of $h$ and use that signed measures of total mass $0$ have dual norm equal
to total variation against functions of oscillation $\spn(h)$:
\[
\left|\sum_y\bigl(Q'-Q\bigr)(y\mid x,a)h(y)\right|
\le
\spn(h)\,\|Q'(\cdot\mid x,a)-Q(\cdot\mid x,a)\|_{\mathrm{TV}}.
\]
Combining the two bounds gives the claim.
\end{proof}

\begin{lemma}[Deviation-value Lipschitz bound]
\label{lem:deviation-lipschitz}
Fix $\eta\in(0,1)$ and a node $C$. There exists a finite constant $L_{\eta,C}$
such that for every player $i$, every two opponents' kernels
$\sigma_{-i},\tau_{-i}\in\prod_{j\ne i}\Sigma_{j,C}$, and every continuation vector
$v\in[0,d_\eta(C)-1]^{B_C\times N}$,
\[
\bigl|\operatorname{Val}_{i,C}(\tau_{-i},v)-\operatorname{Val}_{i,C}(\sigma_{-i},v)\bigr|
\le L_{\eta,C}\,\|\tau_{-i}-\sigma_{-i}\|_1,
\]
where $\operatorname{Val}_{i,C}(\cdot,v)$ denotes the optimal average reward of the
deviation MDP. One may take
\[
L_{\eta,C}=K_{i,C}(1+2H_\eta),
\]
with $K_{i,C}$ as in \Cref{lem:coeff-affine}.
\end{lemma}

\begin{proof}
Fix $\sigma_{-i}$ and let $(g,h)$ be an optimal Bellman certificate for the MDP with
coefficients induced by $(\sigma_{-i},v)$. By \Cref{prop:bias-span},
$\spn(h)\le 2H_\eta$. Apply \Cref{lem:coefficient-transfer} with the primed
coefficients induced by $(\tau_{-i},v)$. Using the Lipschitz estimates from
\Cref{lem:coeff-affine} yields
\[
\operatorname{Val}_{i,C}(\tau_{-i},v)
\le
\operatorname{Val}_{i,C}(\sigma_{-i},v)
+
K_{i,C}(1+2H_\eta)\,\|\tau_{-i}-\sigma_{-i}\|_1.
\]
Interchanging the roles of $\sigma_{-i}$ and $\tau_{-i}$ gives the reverse
inequality.
\end{proof}


\subsection{Blockwise Bellman inequality}

Fix a fixed point $x^*\in\BR_\eta(x^*)$ and the realized profile
$\sigma_{\eta,\delta,M_*}$ from \Cref{thm:realization}. For a complete scheduled
block $B$ played in node $C$, let $X_{\mathrm{in}}(B)$ denote its entry
phase-state and let $X_{\mathrm{out}}(B)\in\Xi_C^{\mathrm{aug}}$ denote the
terminal augmented state of its live segment. Extend each bias $h_{i,C}^*$ to
$\Xi_C^{\mathrm{aug}}$ by the convention
\[
h_{i,C}^*(\partial_b):=0
\qquad (b\in B_C).
\]

\begin{lemma}
\label{lem:block-bellman}
There exists a constant $C_\eta<\infty$ such that for every complete scheduled
block $B$ with cap $L(B)=|B|\ge M_*$ played in node $C$, every player $i$, and
every unilateral deviation $\tau_i$,
\begin{equation}
\label{eq:block-bellman-ineq}
\begin{aligned}
\E\left[
U_i^{\mathrm{full}}(B;\tau_i,\sigma_{-i})
\Bigm|\cF_{\mathrm{in}(B)}
\right]
&\le
\E\bigl[U_i^{\mathrm{cem}}(B)\mid\cF_{\mathrm{in}(B)}\bigr]
+
\bigl(g_{i,C}^*+\eta\bigr)\,
\E\bigl[\tau(B)\mid\cF_{\mathrm{in}(B)}\bigr]
\\
&\quad+
h_{i,C}^*(X_{\mathrm{in}}(B))
-
\E\bigl[h_{i,C}^*(X_{\mathrm{out}}(B))\mid\cF_{\mathrm{in}(B)}\bigr].
\end{aligned}
\end{equation}
Here $U_i^{\mathrm{full}}(B;\tau_i,\sigma_{-i})$ denotes the full
scheduled-block payoff when player $i$ deviates inside the launched block $B$
and the others keep the realized profile.
\end{lemma}

\begin{proof}
Fix $B$, $C$, and $i$. The Bellman certificate at the fixed point gives, for
every phase-state $\xi$ and every action $a_i\in A_i(\xi)$,
\begin{align}
\label{eq:exact-bellman-fixed-point}
g_{i,C}^* + h_{i,C}^*(\xi)
\ge {}
&r_{i,C}^{\sigma_{-i,C}^*}(\xi,a_i)
+
\sum_{\xi'\in\Xi_C}Q_{i,C}^{\sigma_{-i,C}^*}(\xi'\mid\xi,a_i)h_{i,C}^*(\xi')
\\
&+
\sum_{b\in B_C}\Lambda_{i,C}^{\sigma_{-i,C}^*}(b\mid\xi,a_i)v_{i,C}^{x^*}(b)
-\eta.
\nonumber
\end{align}
Inside a complete tail block, the compliant players are run by the controller
$\mathcal R_{C,L(B)}^{\sigma_C^*}$. By \Cref{ass:controller-input}, at every live
stage with current phase-state $\xi$ the conditional mixed action of the
nondeviators is exactly $\sigma_{-i,C}^*(\cdot\mid\xi)$. Hence the deviator sees
the exact one-step coefficients
$r_{i,C}^{\sigma_{-i,C}^*}$, $Q_{i,C}^{\sigma_{-i,C}^*}$, and
$\Lambda_{i,C}^{\sigma_{-i,C}^*}$ from
\eqref{eq:exact-bellman-fixed-point}; there is no separate
coefficient-perturbation term in the Bellman summation.

Let $\tau(B)$ be the live stopping time inside the launched block $B$. Summing
the Bellman inequality from the block entry up to time $\tau(B)$ and taking
conditional expectations gives
\begin{align*}
\E\left[\widetilde U_i(B;\tau_i,\sigma_{-i})\Bigm|\cF_{\mathrm{in}(B)}\right]
\le{}&
\bigl(g_{i,C}^*+\eta\bigr)\,
\E\bigl[\tau(B)\mid\cF_{\mathrm{in}(B)}\bigr]
\\
&+
h_{i,C}^*(X_{\mathrm{in}}(B))
-
\E\bigl[h_{i,C}^*(X_{\mathrm{out}}(B))\mid\cF_{\mathrm{in}(B)}\bigr].
\end{align*}
Now add the common cemetery completion $U_i^{\mathrm{cem}}(B)$ from
\eqref{eq:block-cemetery-payoff} and use \eqref{eq:block-full-payoff}. This yields
\eqref{eq:block-bellman-ineq}. The terminal bias term is zero on a cemetery exit
by the extension convention above, and it is the carried-over bias of the
terminal internal state when the live segment ends at its cap.
\end{proof}

\begin{corollary}[Full scheduled-block regret]
\label{cor:block-regret}
There exists a constant $C_\eta<\infty$ such that for every complete scheduled
block $B$ with cap at least $M_*$ played in node $C$, every player $i$, and
every unilateral deviation $\tau_i$,
\begin{equation}
\label{eq:block-regret-ineq}
\begin{aligned}
\E\left[
U_i^{\mathrm{full}}(B;\tau_i,\sigma_{-i})
-
U_i^{\mathrm{full}}(B;\sigma_{\eta,\delta,M_*})
\Bigm|\cF_{\mathrm{in}(B)}
\right]
&\le
(\eta+C_\eta\delta)\,|B|
\\
&\quad+
h_{i,C}^*(X_{\mathrm{in}}(B))
-
\E\bigl[h_{i,C}^*(X_{\mathrm{out}}(B))\mid\cF_{\mathrm{in}(B)}\bigr].
\end{aligned}
\end{equation}
Both terms in \eqref{eq:block-regret-ineq} are full scheduled-block payoffs on
the same launched interval $B$. The cemetery completion
$U_i^{\mathrm{cem}}(B)$ is the same common addend in both evaluations, so the
only nontrivial subtraction occurs on the live first-exit segment.
\end{corollary}

\begin{proof}
Apply \Cref{lem:block-bellman} to the deviator's full scheduled-block payoff on
the launched block $B$. By \eqref{eq:block-full-payoff-realization}, the compliant
controller on that same launched block satisfies
\[
\E\bigl[U_i^{\mathrm{full}}(B;\sigma_{\eta,\delta,M_*})\mid\cF_{\mathrm{in}(B)}\bigr]
\ge
\bigl(g_{i,C}^*-C_\eta\delta\bigr)\,
\E\bigl[\tau(B)\mid\cF_{\mathrm{in}(B)}\bigr]
+
\E\bigl[U_i^{\mathrm{cem}}(B)\mid\cF_{\mathrm{in}(B)}\bigr]
\]
after enlarging $C_\eta$ if necessary. Subtracting this lower bound from
\eqref{eq:block-bellman-ineq} cancels the common cemetery completion and gives
\begin{equation*}
\begin{aligned}
\E\left[
U_i^{\mathrm{full}}(B;\tau_i,\sigma_{-i})
-
U_i^{\mathrm{full}}(B;\sigma_{\eta,\delta,M_*})
\Bigm|\cF_{\mathrm{in}(B)}
\right]
&\le
(\eta+C_\eta\delta)\,
\E\bigl[\tau(B)\mid\cF_{\mathrm{in}(B)}\bigr]
\\
&\quad+
h_{i,C}^*(X_{\mathrm{in}}(B))
-
\E\bigl[h_{i,C}^*(X_{\mathrm{out}}(B))\mid\cF_{\mathrm{in}(B)}\bigr].
\end{aligned}
\end{equation*}
Since $\tau(B)\le |B|$, this implies \eqref{eq:block-regret-ineq}.
\end{proof}

\subsection{Proof of the main theorem}




\begin{proof}[Proof of \Cref{thm:main}]
Fix $\eps>0$. Choose parameters in the order
\[
\eta,\qquad \delta,\qquad M_*,\qquad T_0.
\]

\smallskip
\noindent\textbf{Step 1: fixed point.}
Choose $\eta>0$ with $\eta\le \eps/3$. By
\Cref{thm:kakutani-global}, there exists a fixed point $x^*\in\BR_\eta(x^*)$.

\smallskip
\noindent\textbf{Step 2: bias bound.}
Recall from \Cref{rem:tree-depth} that $D_\eta<\infty$. By
\Cref{lem:kappa-positive}, $\kappa_\eta>0$. Define
\[
H_\eta:=D_\eta\left(1+\frac{\max_D|\Xi_D|-1}{\kappa_\eta}\right).
\]
By \Cref{prop:bias-span}, every fixed-point Bellman bias satisfies
$\|h_{i,C}^*\|_\infty\le H_\eta$.

\smallskip
\noindent\textbf{Step 3: realization accuracy.}
Choose $\delta>0$ such that $C_\eta\delta\le \eps/3$, where $C_\eta$ is the
constant from \Cref{cor:block-regret}. Since the tree is finite, there is a
common cap threshold
\[
L_\eta(\delta):=\max_{C\in\cT_\eta}L_C(\delta)
\]
from \Cref{thm:local-controller}. Freeze a superexponential schedule at a level
$R$ so large that the associated tail cap $M_*=M_R$ satisfies
$M_*\ge L_\eta(\delta)$. Let
$\sigma^\eps:=\sigma_{\eta,\delta,M_*}$ be the realized profile from
\Cref{thm:realization}.

\smallskip
\noindent\textbf{Step 4: horizon threshold.}
Let $K_\eta<\infty$ absorb four finite effects: the telescoping endpoint
remainder over complete tail blocks from \Cref{lem:aggregation}, the finitely many
prelude blocks before the frozen schedule reaches the tail cap $M_*$, and the
initial and final incomplete fragments in the horizon decomposition of complete
scheduled blocks. There is no separate augmented/ordinary discrepancy term in
Version~14, because the full scheduled-block payoff already covers every
scheduled stage of every complete launched block.
Choose $T_0$ so large that
\[
\frac{K_\eta}{T_0}\le \frac{\eps}{3}.
\]

Now fix $T\ge T_0$, an initial state $s$, a player $i$, and a unilateral
deviation $\tau_i$. Let $B_1,\dots,B_m$ be the complete scheduled tail blocks of
the reference launched partition contained in $[1,T]$, listed in chronological
order. By \Cref{rem:strategy-independent-blocks}, these are the common launched
block intervals on which both the compliant and deviating full-block payoffs are
evaluated. The finitely many prelude blocks, before the superexponential schedule
reaches cap $M_*$, contribute at most $K_\eta/T$ to the average regret; this is
absorbed into the $K_\eta/T$ remainder term.

Apply \Cref{cor:block-regret} block by block to the launched tail blocks and sum.
Within each maximal run of consecutive blocks that stay in the same node, the
bias terms telescope because the terminal internal state of one live segment is
exactly the entry state of the next launched block in that same node. Every time
the node changes, the play moves to a strict child, and this can happen at most
$D_\eta$ times. Therefore \Cref{lem:aggregation}, applied with block lengths
$L_r:=|B_r|$, gives
\[
\frac1T\E\left[\sum_{r=1}^m
\bigl(
U_i^{\mathrm{full}}(B_r;\tau_i,\sigma^\eps_{-i})
-
U_i^{\mathrm{full}}(B_r;\sigma^\eps)
\bigr)\right]
\le
\eta + C_\eta\delta + \frac{K_\eta}{T}.
\]

By construction of the full scheduled-block payoff, on every complete launched
block the quantity $U_i^{\mathrm{full}}$ is exactly the raw payoff over all
scheduled stages of that block. Hence, for both the deviating evaluation
$(\tau_i,\sigma^\eps_{-i})$ and the compliant evaluation $\sigma^\eps$, the only
difference between the horizon-$T$ average payoff and the normalized sum of
complete-block full payoffs comes from the initial and final incomplete
fragments, already absorbed into $K_\eta/T$. Enlarging $K_\eta$ once if
necessary, we obtain
\[
\gamma_i^T\bigl(s,(\tau_i,\sigma^\eps_{-i})\bigr)
-
\gamma_i^T(s,\sigma^\eps)
\le
\eta + C_\eta\delta + \frac{K_\eta}{T}.
\]
By construction, the right-hand side is at most
\[
\frac{\eps}{3}+\frac{\eps}{3}+\frac{\eps}{3}=\eps.
\]
Therefore
\[
\gamma_i^T(s,\sigma^\eps)
\ge
\gamma_i^T\bigl(s,(\tau_i,\sigma^\eps_{-i})\bigr)-\eps.
\]
Since $T\ge T_0$, $s$, $i$, and $\tau_i$ were arbitrary, $\sigma^\eps$ is a
public finite-memory uniform $\eps$-equilibrium.
\end{proof}

\section{Discussion}

The full Neyman conjecture remains open. What the present paper does is narrower
but mathematically sharp: it shows that the downstream compact-tree route is
correct once the finite universal $\eta$-tree object and its first-exit controller
realization are available and once the nodewise irreducibility obstruction from
condition~\textnormal{(a)} is excluded.

The central conceptual distinction in v14 is fourfold: bookkeeping versus
execution, degenerate terminal nodes instead of terminal labels, scheduled block
boundaries versus live first-exit times, and live renewal-reward versus full
scheduled-block payoff. The restart kernel $\rho_C$ belongs only to the convex
bookkeeping package; it is not an executed transition after a cemetery hit.
Execution takes place on the genuine absorbing augmented kernel, the live segment
ends at the first cemetery state, and the local identity remains renewal-reward:
the bookkeeping rates determine $g_{i,C}^*$, while the executed controller
contributes that gain through total augmented live reward divided by actual
first-exit time. Version~14 adds the missing full scheduled-block payoff
identity: once a launched block records a public exit label, the absorbed
cemetery state fills the remaining scheduled stages with the fixed continuation
rate attached to that label, so the full block payoff is the live augmented
reward plus an explicit cemetery completion. In the blockwise regret
subtraction that cemetery completion is a common addend, and the global regret
bound is therefore normalized by the common launched block lengths rather than by
profile-dependent live durations. When a block records a boundary label leading
to a degenerate terminal node $T_b$, the next scheduled block is simply played in
$T_b$, whose gain is exactly $w(b)$ and whose bias is zero. The block schedule
therefore continues through terminal behavior instead of stopping before the
horizon analysis is finished, and no separate post-terminal or post-cemetery
accounting remains outside the common launched block system. With those
distinctions in place, the fixed-point domain is convex, the Bellman target
matches the realized live first-exit segment, the full-block regret comparison is
performed on common scheduled intervals, and the final horizon estimate is an
ordinary telescoping argument on scheduled block lengths.

\appendix


\section{Finite average-reward MDP facts}
\label{app:mdp}

This appendix records the one-player linear-program facts used in the main text.
All statements are standard; see Puterman's monograph \cite{Puterman1994} for
background.

Consider a finite average-reward MDP with state space $X$, action sets $A(x)$,
bounded reward function $r(x,a)\in[0,\overline r]$ for some $\overline r<\infty$,
and transition kernel $Q(\cdot\mid x,a)$.

\begin{proposition}[Primal-dual formulation]
\label{prop:mdp-duality}
The optimal average reward is the common value of the primal and dual linear
programs
\begin{align*}
\textnormal{maximize }&\sum_{x\in X}\sum_{a\in A(x)}\nu(x,a)r(x,a)
\\
\textnormal{subject to }&\nu\ge 0,
\qquad \sum_{x,a}\nu(x,a)=1,
\\
&\sum_{a\in A(y)}\nu(y,a)=\sum_{x,a}\nu(x,a)Q(y\mid x,a)
\qquad (y\in X),
\end{align*}
and
\begin{align*}
\textnormal{minimize }&g
\\
\textnormal{subject to }&g+h(x)\ge r(x,a)+\sum_y Q(y\mid x,a)h(y)
\qquad (x\in X,\ a\in A(x)).
\end{align*}
There exists an optimal stationary mixed policy and an optimal dual pair $(g,h)$.
Moreover, after the linear normalization $h(x^\circ)=0$ at any fixed reference
state $x^\circ\in X$, one may choose $h$ in a compact box.
\end{proposition}

\begin{proof}
This is the classical average-reward LP formulation for finite MDPs. Feasibility is
immediate. The primal feasible set is a nonempty compact polytope, so an optimum
exists. The dual feasible set is nonempty because choosing $g=\overline r$ and
$h\equiv 0$ is feasible. Finite-dimensional LP duality gives equality of primal
and dual
optima and existence of optimal primal and dual solutions. The occupation measure
of an optimal primal solution induces an optimal stationary mixed policy. The
normalization $h(x^\circ)=0$ is obtained by subtracting the constant $h(x^\circ)$.
\end{proof}

\begin{proposition}[Uniqueness of the normalized bias in the communicating case]
\label{prop:bias-unique}
If the finite average-reward MDP is communicating, then any two optimal bias
vectors differ by a constant. Consequently, after fixing one reference coordinate
$h(x^\circ)=0$, the optimal bias is unique.
\end{proposition}

\begin{proof}
This is the standard communicating-MDP relative-value theorem; see
\cite[Chapter~8]{Puterman1994}. In the communicating case the optimal average
reward is state-independent and every optimal bias vector is unique up to an
additive constant. Fixing one coordinate removes that one-dimensional freedom.
\end{proof}


\section{Aggregating block estimates}
\label{app:aggregation}

\begin{lemma}
\label{lem:aggregation}
Let $B_1,\dots,B_m$ be the complete scheduled blocks contained in $[1,T]$,
listed in chronological order. For each $r$, let $C_r$ be the launch node of
$B_r$, let $L_r:=|B_r|$ be its scheduled length, and let $\Delta_r$ be a
block contribution.
Assume there exist constants $a\ge 0$, $H\ge 0$, $D\in\N$, and $K<\infty$ such that:
\begin{enumerate}[label=\textnormal{(\roman*)},leftmargin=2.6em]
\item $\sum_{r=1}^m L_r\le T$;
\item for every $r$ there exist $\cF_{\mathrm{in}(B_r)}$-measurable random variables
$\Psi_r$ and $\widetilde\Psi_r$ with $|\Psi_r|,|\widetilde\Psi_r|\le H$ a.s. and
\[
\E\bigl[\Delta_r\mid \cF_{\mathrm{in}(B_r)}\bigr]
\le
a\,L_r
+
\Psi_r-\E\bigl[\widetilde\Psi_r\mid \cF_{\mathrm{in}(B_r)}\bigr];
\]
\item whenever $B_r$ and $B_{r+1}$ lie in the same node, one has
$\widetilde\Psi_r=\Psi_{r+1}$ almost surely;
\item the number of indices $r$ for which $C_{r+1}\neq C_r$ is at most $D$;
\item the incomplete fragments outside the complete blocks contribute at most $K$
in expectation.
\end{enumerate}
Then
\[
\frac1T\E\left[\sum_{r=1}^m \Delta_r\right]
\le a + \frac{2(D+1)H+K}{T}.
\]
\end{lemma}

\begin{proof}
Partition $B_1,\dots,B_m$ into maximal consecutive runs on which the node is
constant. By assumption~(iv), there are at most $D+1$ such runs. Summing the
conditional estimates from assumption~(ii) and then taking expectations gives
\[
\E\left[\sum_{r=1}^m \Delta_r\right]
\le
a\sum_{r=1}^m L_r
+
\sum_{\text{runs}}
\bigl(\text{initial potential} - \text{terminal potential}\bigr).
\]
Within each run, the intermediate potentials cancel by assumption~(iii). Each run
therefore leaves at most one initial and one terminal term, each bounded in
absolute value by $H$. Because there are at most $D+1$ runs,
\[
\E\left[\sum_{r=1}^m \Delta_r\right]
\le
a\sum_{r=1}^m L_r + 2(D+1)H.
\]
Using assumption~(i) and adding the incomplete-fragment bound from assumption~(v)
yields
\[
\E\left[\sum_{r=1}^m \Delta_r\right]
\le
aT + 2(D+1)H + K.
\]
Divide by $T$.
\end{proof}

\begin{thebibliography}{99}


\bibitem{BewleyKohlberg1976}
T.~Bewley and E.~Kohlberg.
\newblock The asymptotic theory of stochastic games.
\newblock \emph{Mathematics of Operations Research}, 1(3):197--208, 1976.

\bibitem{FleschThuijsmanVrieze1997}
J.~Flesch, F.~Thuijsman, and K.~Vrieze.
\newblock Cyclic {M}arkov equilibria in stochastic games.
\newblock \emph{International Journal of Game Theory}, 26:303--314, 1997.

\bibitem{Kakutani1941}
S.~Kakutani.
\newblock A generalization of {B}rouwer's fixed point theorem.
\newblock \emph{Duke Mathematical Journal}, 8(3):457--459, 1941.

\bibitem{MertensNeyman1981}
J.-F.~Mertens and A.~Neyman.
\newblock Stochastic games.
\newblock \emph{International Journal of Game Theory}, 10(2):53--66, 1981.

\bibitem{MertensSorinZamir2003}
J.-F.~Mertens, S.~Sorin, and S.~Zamir.
\newblock Stochastic games.
\newblock In R.~Aumann and S.~Hart, editors, \emph{Handbook of Game Theory with
Economic Applications}, volume~3, chapter~47, pages 1811--1832. Elsevier,
Amsterdam, 2003.

\bibitem{Neyman2003}
A.~Neyman.
\newblock From {M}arkov chains to stochastic games.
\newblock In A.~Neyman and S.~Sorin, editors, \emph{Stochastic Games and
Applications}, NATO Science Series C, volume~570, pages 9--25. Kluwer Academic
Publishers, Dordrecht, 2003.

\bibitem{Nowak2003}
A.~S.~Nowak.
\newblock N-person stochastic games: Extensions of the finite state space case and
correlation.
\newblock In A.~Neyman and S.~Sorin, editors, \emph{Stochastic Games and
Applications}, NATO Science Series C, volume~570, pages 93--106. Kluwer Academic
Publishers, Dordrecht, 2003.

\bibitem{Puterman1994}
M.~L.~Puterman.
\newblock \emph{Markov Decision Processes: Discrete Stochastic Dynamic
Programming}.
\newblock John Wiley \& Sons, New York, 1994.

\bibitem{Shapley1953}
L.~S.~Shapley.
\newblock Stochastic games.
\newblock \emph{Proceedings of the National Academy of Sciences of the United
States of America}, 39(10):1095--1100, 1953.

\bibitem{Solan1999}
E.~Solan.
\newblock Three-player absorbing games.
\newblock \emph{Mathematics of Operations Research}, 24(3):669--698, 1999.

\bibitem{Solan2003}
E.~Solan.
\newblock Uniform equilibrium: More than two players.
\newblock In A.~Neyman and S.~Sorin, editors, \emph{Stochastic Games and
Applications}, NATO Science Series C, volume~570, pages 285--294. Kluwer Academic
Publishers, Dordrecht, 2003.

\bibitem{SolanVieille2002}
E.~Solan and N.~Vieille.
\newblock Correlated equilibrium in stochastic games.
\newblock \emph{Games and Economic Behavior}, 38(2):362--399, 2002.

\bibitem{Vieille2000I}
N.~Vieille.
\newblock Equilibrium in two-person stochastic games {I}: A reduction.
\newblock \emph{Israel Journal of Mathematics}, 119:55--91, 2000.

\bibitem{Vieille2000II}
N.~Vieille.
\newblock Equilibrium in two-person stochastic games {II}: The case of recursive
games.
\newblock \emph{Israel Journal of Mathematics}, 119:93--126, 2000.

\bibitem{Vieille2002}
N.~Vieille.
\newblock Stochastic games: Recent results.
\newblock In R.~Aumann and S.~Hart, editors, \emph{Handbook of Game Theory with
Economic Applications}, volume~3, chapter~48, pages 1833--1850. Elsevier,
Amsterdam, 2002.

\end{thebibliography}

\end{document}
